---
title: "Risk-stratified COVID-19 policy analysis for Los Angeles County through an integrated risk and stochastic epidemiological model"
subtitle: "Reproducible code package"
author: "University of Southern California, Department of Preventive Medicine"
output:
  html_document:
    css: "styles.css"
    toc: true
    toc_depth: 2
    toc_float: true
editor_options: 
  chunk_output_type: console
---


<!--Initialize-->

``` {r setup, include=FALSE}

### Install necessary packages and get started

library(reshape2)
library(tidyverse)
library(ggplot2)
library(plotly)
library(ggrepel)
library(bindata)
library(odin)
library(fitR)
library(knitr)
library(EasyABC)
library(gridExtra)
library(odin)
library(lubridate)
library(EasyABC)
library(gridExtra)
library(kableExtra)
library(plyr)
library(dplyr)
library(data.table)
library(scales)
library(EasyABC)
library(patchwork)

library(tidyr)
library(readr)
library(purrr)
library(tibble)
library(stringr)
library(forcats)
library(network)
library(tidygraph)
library(ggraph)
library(visNetwork)
library(networkD3)
library(ggmosaic)
library(formattable)
library(DT)
library(reshape)
library(here)
library(fs)

library(MASS)
library(plotly)

lang_output <- function(x, lang) {
  cat(c(sprintf("```%s", lang), x, "```"), sep = "\n")
}
r_output <- function(x) lang_output(x, "r")

knitr::opts_chunk$set(
  fig.width = 9.5,
  fig.height = 8,
  eval=TRUE,
  echo=FALSE,
  warning=FALSE,
  cache=FALSE,
  message=FALSE,
  include=TRUE
  )

code.dir=here("code/")
data.dir=here("data/")
result.dir = here("results/")
fig.dir = here("figs/")
output.dir = here("output/")
code.paper.dir=here("code/epi_model_code")
code.risk.dir=here("code/risk_model_code/")
code.scenarios.dir=here("code/scenarios_code/")
```

<!--Set global options-->

```{r options, include=FALSE}
print.output <- FALSE
days.truncate <- 15
endDatePlot <- as.Date("2020-10-15")
```


<!--Read in epidemic model, functions, COVID data-->

```{r read-in-model-supporting-functions, include=FALSE}

###################################################################################################
## LOAD EPIDEMIC MODEL
## And compile the model
path_seihqdr_model <- path(code.paper.dir, "stochastic_SEIAHQDR_Alphat_rt.R")
seihqdr_generator <- odin::odin(path_seihqdr_model)

###################################################################################################
## LOAD DATA PROCESSING AND MODEL ESTIMATING FUNCTIONS
model_functions <- path(code.paper.dir, "data_model_fun.R")
source(model_functions)

###################################################################################################
## LOAD PLOTTING FUNCTIONS
plot_code <- path(code.paper.dir, "plotting_fun_NEW.R")
source(plot_code)

###################################################################################################
## LOAD TABLES FUNCTIONS
tables_code <- path(code.paper.dir, "tables_fun.R")
source(tables_code)

###################################################################################################
## COVID INPUT DATA
# latest_data: cumulative and daily counts for "Htotcum","D","Vcum","Idetectcum","H_new","D_new"
# no_obs: number of observation days
latest_data <- latest_covid_data(truncate=days.truncate)
no_obs <- nrow(latest_data)

```


<!--Model Fitting-->

```{r include=FALSE}

## SOURCE PRIOR PARAMETERS
## Provides output in form of a prior.par list
## Note: Beta(t), Alpha(t), Kappa(t), Delta(t) are read in from file
prior_param_input <- path(code.paper.dir, "prior_param.R")
source(prior_param_input)
# prior.par

## SUMMARY STATISTICS COMPUTED ON DATA
summarydata <- sum.stats.SIMTEST(latest_data,include.R = FALSE)
model.R <- model.1sim.stats.no.R  # From supporting_functions

### NUMBER OF OUTPUTS
# n_calibration = 10000
# n_rec = 2000

n_calibration = 1000
n_rec = 100

## FIT MODEL
ABC_out<-ABC_mcmc(method="Marjoram",model=model.R,prior=prior.par,
                       summary_stat_target=summarydata, n_calibration=n_calibration,
                       tolerance_quantile=0.1,verbose=FALSE,progress=TRUE, n_rec=n_rec)

ABC.par.out <- as.data.frame(ABC_out$param)
ABC.out.mat <- ABC_out$param
par.vec.length <- nrow(ABC_out$param)

```


<!--Simulate model-->
<!--Get compartment variables over time with CI-->
<!--Get CFR/IFR-->

```{r include=FALSE}
###################################################################################################
## GET MODEL OUTPUT: traj.0

ABC.out.mat <- ABC_out$param
par.vec.length <- nrow(ABC_out$param)
iter <- 10
time.steps <- 400
vars.to.plot <- vars.plus.R

## FUNCTION MODEL.OUTPUT.TO.PLOT.SIM
## Calculates mean and CI of each estimated parameter & CFR/IFR
## Uses correlated.param.SIM
## Reads in Beta, Alpha, Kappa, Delta from file
traj.0 <- model.output.to.plot.SIM(ABC.out.mat=ABC.out.mat, par.vec.length=par.vec.length, iter=iter, time.steps=time.steps, vars.to.plot = vars.to.plot)

```

# Epidemic model

## Tables: Parameter estimates {.tabset}

```{r include=FALSE}
###################################################################################################
## GET MODEL OUTPUT: summary

startDatePlot <- as.Date("2020-03-01")
#endDatePlot <- as.Date("2020-12-01")
all_day_1s <- seq(startDatePlot,endDatePlot,by='month')
all_day_15s <- all_day_1s+14
date.in <- sort(c(all_day_1s,all_day_15s))
tables.out <- summary.table.param.CFR.IFR(traj.CI=traj.0, ABC_out=ABC_out, date.in=date.in, use.mean.select = 1, round.by.in=4)

```

### $R0$, $r(t)$, $\mu(t)$
```{r}
formattable(tables.out[[1]])
if (print.output==TRUE) write.csv(tables.out[[1]], file = path(output.dir, "R.r.mu_table.csv"))
```

### $\alpha(t)$, $\kappa(t)$, $\delta(t)$

```{r}
formattable(tables.out[[2]])
akd_table <- tables.out[[2]]
if (print.output==TRUE) write.csv(tables.out[[2]], file = path(output.dir, "AKD_t_table.csv"))
```

### CFR and IFR

```{r}
formattable(tables.out[[3]])
if (print.output==TRUE) write.csv(tables.out[[3]], file = path(output.dir, "CFR_IFR_table.csv"))
```

## Figure: Model fits

Summarizes the epidemic model fit with COVID-19 data for LAC from March 1 through `r as.Date("2020-03-01") + no_obs` for all disease states across multiple views: New cases, representing new daily incidence; the current number in a compartment at a specific date, relevant for understanding current prevalence rates and comparing with healthcare capacity limitations; and cumulative counts until a specific date. Observed data for available compartments with cases attributable to nursing home residents removed, are plotted as black dots. The figure demonstrates that good model fits are achieved in all compartments across time.

* **New = new daily incidence**
* **Current = current census in compartment** 
* **Cumulative = running total over time**
* Black dots depict COVID-19 data, with counts from outbreaks in nursing homes removed
* The dashed line represents healthcare resource capacity limits

```{r include=FALSE}

###################################################################################################
## Plot all variables faceted

time.steps.4.plot = as.Date("2020-11-15") - as.Date("2020-03-01") + 1
data.in <- latest_data
vars.to.plot <- vars.plus.R

plot.all.variables <- 
plot.model.data.all(traj.CI = traj.0, data.in = data.in, init.date.data = "2020-03-01", date.offset.4plot = 15, time.steps.4plot=time.steps.4.plot,
                    vars.to.plot=vars.plus.R)

if (print.output==TRUE){
  pdf(file = path(output.dir, "plot.all.variables.pdf"), width=10, height =10)
  plot.all.variables
  dev.off()
}

```

```{r}
plot.all.variables
```


## Figures: Time-Varying Parameters {.tabset}

```{r include=FALSE}

#endDatePlot <- as.Date("2020-12-01")
Fig3.plots <- plot.param.t(ABC_out = ABC_out, endDatePlot=endDatePlot)

if (print.output==TRUE){
  pdf(file = path(output.dir, "plot_Rt.pdf"), width=10, height =10)
  Fig3.plots[[1]]
  dev.off()
  
  pdf(file = path(output.dir, "plot_r_t.pdf"), width=10, height =10)
  Fig3.plots[[2]]
  dev.off()
  
  pdf(file = path(output.dir, "plot_AKD_t.pdf"), width=10, height =10)
  Fig3.plots[[3]]
  dev.off()
}

```

### Reproductive Number $R(t)$

```{r}
Fig3.plots[[1]]
```

### Fraction of Observed Infections $r(t)$

```{r}
Fig3.plots[[2]]
```

### $\alpha(t)$, $\kappa(t)$, $\delta(t)$

```{r}
Fig3.plots[[3]]
```

<!--CFR and IFR-->

```{r include=FALSE}

startDatePlot <- as.Date("2020-03-01")
#endDatePlot <- as.Date("2020-12-01")
all_day_1s <- seq(startDatePlot,endDatePlot,by='month')
all_day_15s <- all_day_1s+14
date.in <- sort(c(all_day_1s,all_day_15s))

CFR.IFR.plots.out <- CFR.IFR.plots(traj.CI=traj.0, date.in=date.in, endDatePlot = endDatePlot)

if (print.output==TRUE){
  pdf(file = path(output.dir, "CFR_plot.pdf"), width=10, height =10)
  CFR.IFR.plots.out[[1]]
  dev.off()
  
  pdf(file = path(output.dir, "IFR_plot.pdf"), width=10, height =10)
  CFR.IFR.plots.out[[2]]
  dev.off()
}
```

### Time-varying CFR(t)

```{r}
CFR.IFR.plots.out[[1]]
```

### Time-varying IFR(t)
```{r}
CFR.IFR.plots.out[[2]]
```


## Figures: Compartmental Variables {.tabset}

```{r include=FALSE}

## Get compartmental variable plots TOGETHER and print/save
plot.out.H.I <- plot.out.compartmental(traj.CI = traj.CI, endDatePlot = as.Date("2020-11-01"))

if (print.output==TRUE){
  pdf(file = path(output.dir, "curr_infect_TOGETHER.pdf"), width=10, height =10)
  plot.out.H.I[[2]]
  dev.off()
  
  pdf(file = path(output.dir, "curr_healthcare_TOGETHER.pdf"), width=10, height =10)
  plot.out.H.I[[1]]
  dev.off()
}

## Get compartmental variable plots INDIVIDUALLY and print/save
# plot.compartments.out <- plot.compartments(traj.CI.in = traj.0)
# curr.infect.variables <- plot.compartments.out[[1]]
# curr.healthcare.variables <- plot.compartments.out[[2]]
# 
# if (print.output==TRUE){
#   pdf(file = path(output.dir, "curr_infect_var.pdf"), width=10, height =10)
#   curr.infect.variables
#   dev.off()
#   
#   pdf(file = path(output.dir, "curr_healthcare_var.pdf"), width=10, height =10)
#   curr.healthcare.variables
#   dev.off()
# }

## Get plots for individual variables (for ggplotly)
time.steps.4plot <- as.numeric(endDatePlot - as.Date("2020-03-01"))

var.to.plot <- "I"
ymax=100000
plot.I <- plot.model.single(traj.CI=traj.0, data.in=data.in, init.date.data="2020-03-01", date.offset.4plot=0, 
                           time.steps.4plot=time.steps.4plot, ymax=ymax, plot.capacity=NULL,var.to.plot=var.to.plot,
                           use.title=NULL, scenario=scenario, intervention_date=intervention_date, sd.redux=NULL)

var.to.plot <- "Itot"
ymax=200000
plot.Itot <- plot.model.single(traj.CI=traj.0, data.in=data.in, init.date.data="2020-03-01", date.offset.4plot=0, 
                           time.steps.4plot=time.steps.4plot, ymax=ymax, plot.capacity=NULL,var.to.plot=var.to.plot,
                           use.title=NULL, scenario=scenario, intervention_date=intervention_date, sd.redux=NULL)
var.to.plot <- "Htot"
ymax = 3000
plot.Htot <- plot.model.single(traj.CI=traj.0, data.in=data.in, init.date.data="2020-03-01", date.offset.4plot=0, 
                           time.steps.4plot=time.steps.4plot, ymax=ymax, plot.capacity=NULL,var.to.plot=var.to.plot,
                           use.title=NULL, scenario=scenario, intervention_date=intervention_date, sd.redux=NULL)

var.to.plot <- "D_new"
ymax = 200
plot.Dnew <- plot.model.single(traj.CI=traj.0, data.in=data.in, init.date.data="2020-03-01", date.offset.4plot=0, 
                           time.steps.4plot=time.steps.4plot, ymax=ymax, plot.capacity=NULL,var.to.plot=var.to.plot,
                           use.title=NULL, scenario=scenario, intervention_date=intervention_date, sd.redux=NULL)

```

### Current observed and total infections

```{r}
plot.out.H.I[[2]]
```

### Current hospitalizations, ventilations, and new deaths

```{r}
plot.out.H.I[[1]]
```

### Current observed infections

```{r}
ggplotly(plot.I)
```

### Current estimated total infections

```{r}
ggplotly(plot.Itot)
```


### Current in hospital

```{r}
ggplotly(plot.Htot)
```

### New deaths

```{r}
ggplotly(plot.Dnew)
```

{-}



# Risk model

<!--- 
Read in data
--->

```{r include=FALSE}
###############################################################################################################
## Read in marginal risk probability P(H|I), P(Q|H), P(D|Q) for each risk profile q, calculated by the JAM model
## Data coming from: Guan et al. 2020, Petrilli et al. 2020
Pr.H <- read.csv(path(data.dir, "Pr.H.csv"), sep=",", header=TRUE,row.names = 1)
Pr.Q <- read.csv(path(data.dir, "Pr.Q.csv"), sep=",", header=TRUE,row.names = 1)
Pr.D <- read.csv(path(data.dir, "Pr.D.csv"), sep=",", header=TRUE,row.names = 1)

## Get profile matrix X.mat
X.mat <- as.matrix(dplyr::select(Pr.H, -1))
n_factors <- ncol(X.mat)
n_profiles <- nrow(X.mat)

#########################################################################################################
## Read in prevalence of each risk factor p in the population for LA County
## Data coming from:
#### [Los Angeles County Health Survey](http://www.publichealth.lacounty.gov/ha/hasurveyintro.htm)
#### [California Health Information Survey](http://ask.chis.ucla.edu)
Pop.prevalence <- read.csv(path(data.dir, "Pop.prevalence.LA.csv"), sep=",", header=TRUE,row.names = 1 )
Pop.prev.matrix<-as.matrix(Pop.prevalence)

#########################################################################################################
## Read in correlation structure, $\Sigma$, between the risk factors p
## Correlation structure is weighted according to the prevalence of each race/ethnicity in LA County
## Calculated using data coming from: The National Health and Nutrition Examination Survey (NHANES)
SIGMA <- read.csv(path(data.dir, "SIGMA.csv"), sep=",", header=TRUE,row.names = 1)

```

<!---
Calculate prevalence of each profile in overall LAC population
--->

```{r riskprofiles, include=FALSE, eval=TRUE}
calc_profile_prev<- path(code.risk.dir, "calc_profile_prev.R")
source(calc_profile_prev)

## OUTPUT
# profile.cnt.freq
```

<!---
Estimate risk probabilities with baseline from epidemic model
--->

```{r estimate-risk-integrated}

##################################################
## INPUTS: TIMES
### Chosen times to run analysis at
t1 <- "2020-05-15"
t2 <- "2020-08-01"
t3 <- "2020-10-15"
table.dates <- c("May.15","Aug.1","Oct.15")
times <- c("t1", "t2", "t3")
times.dates <- as.Date(c(t1,t2,t3))

# t1 <- "2020-05-15"
# t2 <- "2020-07-15"
# t3 <- "2020-09-15"
# t4 <- "2020-10-15"
# table.dates <- c("May.15","Jul.15","Sep.15","Oct.15")
# times.dates <- as.Date(c(t1,t2,t3,t4))
# times <- c("t1","t2","t3","t4")

n.times <- length(times)

##################################################
## INPUTS: OBSERVED LAC DATA ON ILLNESSES
### Observed LAC age prevalence in (I) infections
n.dates.LAC.obs.age <- length(times)
freq.LAC.obs.age <- matrix(nrow=3, ncol=n.dates.LAC.obs.age)
colnames(freq.LAC.obs.age) <- times
rownames(freq.LAC.obs.age) <- c("Age0.19","Age20.64","Age65.")
# freq.LAC.obs.age[,1] <- c(0.011, 0.750, 0.239)  # Apr15
# freq.LAC.obs.age[,2] <- c(0.080, 0.799, 0.121)  # Jul15
# freq.LAC.obs.age[,3] <- c(0.102, 0.784, 0.114)  # Oct15
# freq.LAC.obs.age[,1] <- c(0.035, 0.749, 0.216)  # May15
# freq.LAC.obs.age[,2] <- c(0.080, 0.799, 0.121)  # Jul15
# freq.LAC.obs.age[,3] <- c(0.099, 0.785, 0.116)  # Sep15
# freq.LAC.obs.age[,4] <- c(0.102, 0.784, 0.114)  # Oct15
freq.LAC.obs.age[,1] <- c(0.035, 0.749, 0.216)  # May.15
freq.LAC.obs.age[,2] <- c(0.089, 0.791, 0.120)  # Aug.1
freq.LAC.obs.age[,3] <- c(0.102, 0.784, 0.114)  # Oct.15


##################################################
## INPUTS: EPIDEMIC MODEL
## Get mean estimates of Alpha(t), Kappa(t), Delta(t) at each time point 
akd_table <- tables.out[[2]]
table1 <- akd_table
for (i in 1:2){  table1[i,] <- akd_table[i,] %>% mutate_if(is.character, function(x) unlist(strsplit(x, " "))[1])}
table1 <- as.data.frame(apply(table1, 2, as.numeric)) 

## Create extra rows representing Alpha, Kappa, Delta values for t > 2 (with same values for Alpha, Kappa, Delta as t2)
if (n.times > 2){ for (exrow in 3:n.times) table1[exrow,] <- table1[2,] }
rownames(table1) <- times
risk.probs.POSTERIORS <- table1

##################################################
## INPUTS: PROFILE FREQUENCY
### Estimated frequency of each risk profile
freq.PREV.q <- as.vector(profile.cnt.freq[,1])

##################################################
## INPUTS: JAM ESTIMATED CONDITIONAL RISK EFFECTS
### Read in JAM produced conditional effect estimates
psi.mat = read.csv(path(data.dir, "psi.conditional.effect.estimates.csv"), sep=",", header=TRUE,row.names = 1)
rownames(psi.mat) <- colnames(X.mat)
psi.mat[1,] <- c(rep(-1,times=3))

##################################################
## APPLY CODE TO GET ESTIMATE RISK PROBABILITIES WITH BASELINE FROM EPIDEMIC MODEL
calc_integrated_risk_model<- path(code.risk.dir, "integrated_risk_model.R")
source(calc_integrated_risk_model)

Pr.freq.FUN.out <- Pr.freq.FUN(X.mat=X.mat, freq.PREV.q = freq.PREV.q, 
                               freq.LAC.obs.age=freq.LAC.obs.age, logit.SEIR.est=logit.SEIR.est,psi.mat=psi.mat)
### OUTPUTS
Pr.OUT <- Pr.freq.FUN.out[[1]]
freq.OUT <- Pr.freq.FUN.out[[2]]   

```

<!---
Clean data and get function for CFR and IFR table
--->

```{r clean-data-get-CFR, include=FALSE}

## INPUTS
#X.mat
#Pr.OUT
#freq.OUT

clean_data_risk_estimates_LAC <- path(code.risk.dir,"clean_data_integrated_risk.R")
source(clean_data_risk_estimates_LAC)

## OUTPUTS
#data.prev #used for CFR/IFR calculation

## Note: The 5 risk groups are assigned within this code
##       Currently are grouped according to CFR.t1
##       To modify the risk grouping cutoffs see the end of this code.
```

<!---
Table: CFR and IFR by risk profile
--->

```{r risk_table_ALL_COLUMNS_INCLUDED, include=FALSE}

########################################################################
## risk.table.CFR.fn code found in clean_data_risk_estimates.R
# Requires data.prev from clean_data_risk_estimates_LAC
########################################################################

ABC.out.mat <- ABC_out$param
time.steps = 400
iter <- 10
round.by <- 4
times.dates <- times.dates
filter.by <- 0.00001

## Get CFR/IFR output
risk_table_CFR_FULL <- risk.table.CFR.IFR.dates(ABC.out.mat=ABC.out.mat, time.steps=time.steps, iter=iter, data.prev=data.prev, times.dates=times.dates, round.by=round.by)

## Format CFR/IFR table
risk_table_CFR <- CFR_to_print(risk_table_CFR_FULL = risk_table_CFR_FULL, table.dates=table.dates, times.dates=times.dates, round.by=round.by, filter.by=filter.by)

# Save output
if (print.output==TRUE) write.csv(risk_table_CFR, file = path(output.dir, "CFR_IFR_table_FULL.csv"))

# Create as a formattable
unit.scale = function(x) (x - min(x)) / (max(x) - min(x))

risk_table_CFR.FT <- formattable(risk_table_CFR, align="c",
            #align = c(rep("c", 9)),
            list(
  `age`= color_tile('yellow', 'darkorange'),
  `BMI`= color_tile('lightblue', 'pink'),
  `smoking`= color_tile('grey', 'transparent'),
  `comorbidity`= color_tile('darkgrey', 'transparent'),
  `Group`= color_tile('red', 'green'),
  `Pop.Prev`= color_bar('cornflowerblue', fun = unit.scale),
    `Inf.May.15`= color_bar('orchid', fun = unit.scale),
  `Inf.Aug.1`= color_bar('plum', fun = unit.scale),
  `Inf.Oct.15`= color_bar('lightpink', fun = unit.scale),
  `CFR.May.15`= color_bar('orchid', fun = unit.scale),
  `CFR.Aug.1`= color_bar('plum', fun = unit.scale),
  `CFR.Oct.15`= color_bar('lightpink', fun = unit.scale),
  `IFR.May.15`= color_bar('orchid', fun = unit.scale),
  `IFR.Aug.1`= color_bar('plum', fun = unit.scale),
  `IFR.Oct.15`= color_bar('lightpink', fun = unit.scale)
))

#risk_table_CFR.FT

## FILTERED TO ONLY THOSE PROFILES WITH PREVALENCE > 1%
## FOR PRINTING IN PAPER
# risk_table_CFR_filtered.FT <- formattable(risk_table_CFR %>% filter(Pop.Prev > 0.01), 
#                                           align="c",
#             #align = c(rep("c", 9)),
#             list(
#   `age`= color_tile('yellow', 'darkorange'),
#   `BMI`= color_tile('lightblue', 'pink'),
#   `smoking`= color_tile('grey', 'transparent'),
#   `comorbidity`= color_tile('darkgrey', 'transparent'),
#   `Group`= color_tile('indianred4', 'green'),
#   `Pop.Prev`= color_bar('cornflowerblue', fun = unit.scale),
#     `Inf.May.15`= color_bar('orchid', fun = unit.scale),
#   `Inf.Aug.1`= color_bar('plum', fun = unit.scale),
#   `Inf.Oct.15`= color_bar('lightpink', fun = unit.scale),
#   `CFR.May.15`= color_bar('orchid', fun = unit.scale),
#   `CFR.Aug.1`= color_bar('plum', fun = unit.scale),
#   `CFR.Oct.15`= color_bar('lightpink', fun = unit.scale),
#   `IFR.May.15`= color_bar('orchid', fun = unit.scale),
#   `IFR.Aug.1`= color_bar('plum', fun = unit.scale),
#   `IFR.Oct.15`= color_bar('lightpink', fun = unit.scale)
# ))

```

<!---
Table: Probabilities of severe illness by risk profile
--->

```{r probabilities-table, include=FALSE}

########################################################################
# Probabilities of severe illness by risk profile table
# Requires risk_table_CFR_FULL and Profiles and Pr.OUT
########################################################################

# Get and format probability table
probs_table_FULL <- probs_to_print(risk_table_CFR_FULL=risk_table_CFR_FULL, Profile=Profile,Pr.OUT=Pr.OUT,table.dates=table.dates, times.dates=times.dates, round.by=round.by, filter.by=filter.by)

# Save output
if (print.output==TRUE) write.csv(probs_table_FULL, file = path(output.dir, "probs_table_FULL.csv"))

########################################################################
## Create as a formattable
########################################################################

probs_table_FULL.FT <- formattable(probs_table_FULL, align="c",
            #align = c(rep("c", 9)),
            list(
  `age`= color_tile('yellow', 'darkorange'),
  `BMI`= color_tile('lightblue', 'pink'),
  `smoking`= color_tile('grey', 'transparent'),
  `comorbidity`= color_tile('darkgrey', 'transparent'),
  `Group`= color_tile('red', 'green'),
  `Pop.Prev`= color_bar('cornflowerblue', fun = unit.scale),
    `P(H|I).May.15`= color_bar('orchid', fun = unit.scale),
  `P(H|I).Aug.1`= color_bar('plum', fun = unit.scale),
  `P(H|I).Oct.15`= color_bar('lightpink', fun = unit.scale),
  `P(Q|H).May.15`= color_bar('orchid', fun = unit.scale),
  `P(Q|H).Aug.1`= color_bar('plum', fun = unit.scale),
  `P(Q|H).Oct.15`= color_bar('lightpink', fun = unit.scale),
  `P(D|Q).May.15`= color_bar('orchid', fun = unit.scale),
  `P(D|Q).Aug.1`= color_bar('plum', fun = unit.scale),
  `P(D|Q).Oct.15`= color_bar('lightpink', fun = unit.scale)
))

#probs_table_FULL.FT

## FILTERED TO ONLY THOSE PROFILES WITH PREVALENCE > 1%
## FOR PRINTING IN PAPER
# probs_table_filtered.FT <- formattable(probs_table_FULL %>% filter(Pop.Prev>0.01),
#                                    align="c",
#             #align = c(rep("c", 9)),
#             list(
#   `age`= color_tile('yellow', 'darkorange'),
#   `BMI`= color_tile('lightblue', 'pink'),
#   `smoking`= color_tile('grey', 'transparent'),
#   `comorbidity`= color_tile('darkgrey', 'transparent'),
#   `Group`= color_tile('indianred4', 'green'),
#   `Pop.Prev`= color_bar('cornflowerblue', fun = unit.scale),
#     `P(H|I).May.15`= color_bar('orchid', fun = unit.scale),
#   `P(H|I).Aug.1`= color_bar('plum', fun = unit.scale),
#   `P(H|I).Oct.15`= color_bar('lightpink', fun = unit.scale),
#   `P(Q|H).May.15`= color_bar('orchid', fun = unit.scale),
#   `P(Q|H).Aug.1`= color_bar('plum', fun = unit.scale),
#   `P(Q|H).Oct.15`= color_bar('lightpink', fun = unit.scale),
#   `P(D|Q).May.15`= color_bar('orchid', fun = unit.scale),
#   `P(D|Q).Aug.1`= color_bar('plum', fun = unit.scale),
#   `P(D|Q).Oct.15`= color_bar('lightpink', fun = unit.scale)
# ))

```

## Severe illness probabilities by profile

```{r}
probs_table_FULL.FT <- as.datatable(probs_table_FULL.FT, rownames = TRUE, options = list(pageLength = 10, autoWidth = TRUE))
probs_table_FULL.FT
```

## CFR(t) and IFR(t) by profile

```{r}
risk_table_CFR.DT <- as.datatable(risk_table_CFR.FT, rownames = TRUE, options = list(pageLength = 10, autoWidth = TRUE))
risk_table_CFR.DT
```

<!---
Calculate frequency of risk factor groups by stage of disease
Create plots for each risk factor group
--->

```{r get-group-by-stage}

## Source code to clean data and get function for creating "Stage of disease by risk factor group" figures
grouped_fig_code <- path(code.risk.dir, "clean_data_grouped_figs.R")
source(grouped_fig_code)

## Get "Stage of disease by risk factor group" figures
var = "age"
var.name <- "Age"
p.prev.age.stage.DATES <- grouped.var.figs(full.data=full.data, var=var, var.name=var.name, times=times, table.dates=table.dates)

var = "BMI"
var.name <- "Obesity"
p.prev.BMI.stage.DATES <- grouped.var.figs(full.data=full.data, var=var, var.name=var.name, times=times, table.dates=table.dates)

var = "comorbidity"
var.name = "Comorbidity"
p.prev.comorbidity.stage.DATES <- grouped.var.figs(full.data=full.data, var=var, var.name=var.name, times=times, table.dates=table.dates)

var = "smoking"
var.name = "Smoking status"
p.prev.smoking.stage.DATES <- grouped.var.figs(full.data=full.data, var=var, var.name=var.name, times=times, table.dates=table.dates)

p.prev.risk.stage.DATES<- ggplot(full.data, aes(x = stage, y = values, fill = riskprofile)) +
    geom_bar(position="stack", stat = 'identity') + 
    scale_fill_manual("legend", values = c("Risk 1" = "#ff0000", "Risk 2" = "#bf4000", "Risk 3" = "#7f7f00", "Risk 4" = "#40bf00", "Risk 5" = "#00ff00")) + 
    facet_wrap(DATE ~ ., labeller=labeller(DATE = times.names)) +
    labs(title = "Risk Groups by stage of disease", x = NULL, y = "Frequency") +
    scale_x_discrete(labels = c("Prevalence", "Infected", "Hospitalized", "ICU", "Dead")) +
    theme(axis.text.x = element_text(angle = 90))

if (print.output==TRUE){
  tiff(file = path(output.dir, "stage_by_group.tiff"), 
       units="in", width=15, height=8, res=600, compression = 'lzw')
  
  p.prev.risk.stage.DATES + p.prev.age.stage.DATES + p.prev.BMI.stage.DATES +  p.prev.comorbidity.stage.DATES + p.prev.smoking.stage.DATES + plot_annotation(tag_levels = 'A' )
  
  dev.off()
}

```


## Stage of disease by risk factor group {.tabset}

Estimated frequency of groups in the overall LAC population, and the population of individuals in each stage of disease from infected, hospitalized, admitted to ICU, to deceased on each date `r table.dates` (2020): (A) Risk Groups, (B) age group, (C) obesity class groups, (D) any comorbidity group, and (E) smoking status group. 

### Risk group

```{r}
p.prev.risk.stage.DATES
```

### Age

```{r}
p.prev.age.stage.DATES
```

### Cormorbidity

```{r}
p.prev.comorbidity.stage.DATES
```

### BMI

```{r}
p.prev.BMI.stage.DATES
```

### Smoking status

```{r}
p.prev.smoking.stage.DATES
```

{-}



# Scenarios

<!---
Scenarios: Get Alpha, Kappa, Delta with populations protected
--->

```{r scenarios, include=FALSE}

##################################################
## SOURCE SCENARIOS FUNCTIONS
scenarios_functions <- path(code.scenarios.dir, "scenarios_fun.R")
source(scenarios_functions)

##################################################
## INPUTS for getting % removed for various scenarios
percent.to.remove <- c(0,0.5,1) #c(1,0.5,0) 
factor.to.remove <- 4  # Age.65.

##################################################
## Apply function for calculating decrease in Alpha Kappa Delta when protecting/removing 65+ from population

weighted.avg.scenarios.overall <- 
  weighted.avg.protect.SCENARIOS(X.mat=X.mat, freq.PREV.q = freq.PREV.q, 
                                 freq.LAC.obs.age=freq.LAC.obs.age, logit.SEIR.est=logit.SEIR.est,
                                 psi.mat=psi.mat,percent.to.remove=percent.to.remove,
                                 factor.to.remove=factor.to.remove)

##################################################
## Name the scenarios

protect.scenarios.mat <- matrix(NA, nrow=3, ncol=2)
colnames(protect.scenarios.mat) <- c("index","protect.name")
protect.scenarios.mat[,"index"] <- c(1:3)
protect.scenarios.mat[,"protect.name"] <- rownames(weighted.avg.scenarios.overall)
protect.scenarios.mat <- as.data.frame(protect.scenarios.mat)
protect.scenarios.mat

NPI.scenarios.mat <- matrix(NA, nrow=3, ncol=3)
colnames(NPI.scenarios.mat) <- c("index","NPI.name","Beta_y_vals")
NPI.scenarios.mat[,"index"] <- c(1:3)
NPI.scenarios.mat[,"NPI.name"] <- c("NPI.None","NPI.Mod", "NPI.Obs")  #c("NPI.Obs","NPI.Mod","NPI.None")
NPI.scenarios.mat[,"Beta_y_vals"] <- c("Beta_y_nothing", "Beta_y_moderate", "Beta_y" )  #c("Beta_y","Beta_y_moderate","Beta_y_nothing")
NPI.scenarios.mat <- as.data.frame(NPI.scenarios.mat)
NPI.scenarios.mat


##################################################
## Plot the scenario policies to run

plot.scenarios.in <- plot.SCENARIOS.input(ABC_out=ABC_out, 
                                          NPI.scenarios.mat=NPI.scenarios.mat,
                                          protect.scenarios.mat=protect.scenarios.mat, 
                                          weighted.avg.scenarios=weighted.avg.scenarios.overall, 
                                          endDatePlot=endDatePlot)
if (print.output==TRUE){
  pdf(file = path(output.dir, "plot.scenarios.IN.NPI.pdf"), width=10, height =10)
  plot.scenarios.in[[1]]
  dev.off()
  
  pdf(file = path(output.dir, "plot.scenarios.IN.Protect.pdf"), width=10, height =10)
  plot.scenarios.in[[2]]
  dev.off()
}

##################################################
## Run the scenarios

num.to.run = 100
ABC.out.mat.scenarios = ABC.out.mat[c(1:num.to.run),]
iter=10
time.steps=400

correlated.param.SCENARIOS.out <- 
  correlated.param.SCENARIOS(ABC.out.mat=ABC.out.mat.scenarios,iter=iter,time.steps=time.steps,
                             weighted.avg.scenarios=weighted.avg.scenarios.overall,
                             protect.scenarios.mat=protect.scenarios.mat, NPI.scenarios.mat=NPI.scenarios.mat)

##################################################
## Plot the scenarios

data.in <- latest_data %>% select("D")
endDatePlot=as.Date("2020-11-15")
vars.to.plot <- c("Itot","I", "Htot","D","CFRactual","CFRobs")
traj.CI <- correlated.param.SCENARIOS.out
filter.scenarios <- NULL

plot.SCENARIOS.ALL <-  plot.SCENARIOS(traj.CI=traj.CI, data.in=data.in, endDatePlot=endDatePlot, vars.to.plot = vars.to.plot, filter.scenarios=filter.scenarios)

filter.scenarios=c(4:9)
plot.SCENARIOS.filter <-  plot.SCENARIOS(traj.CI=traj.CI, data.in=data.in, endDatePlot=endDatePlot, vars.to.plot = vars.to.plot, filter.scenarios=filter.scenarios)

if (print.output==TRUE){
  pdf(file = path(output.dir, "plot.scenarios.OUT.ALL.pdf"), width=10, height =10)
  plot.SCENARIOS.ALL
  dev.off()
  
  pdf(file = path(output.dir, "plot.scenarios.OUT.filter.pdf"), width=10, height =10)
  plot.SCENARIOS.filter
  dev.off()
}
```

## Scenarios: Policies Run {.tabset}

### NPI scenarios inputs

```{r}
plot.scenarios.in[[1]]
```

### Protect scenarios run

```{r}
plot.scenarios.in[[2]]
```


{-}

## Scenarios: Results

### All scenarios

```{r}
plot.SCENARIOS.ALL
```


### Scenarios with NPI modifications

```{r}
plot.SCENARIOS.filter
```

