---
title: "COVID19 Modeling for Los Angeles County"
subtitle: Analysis updated with data as of `r Sys.Date()`
author: "University of Southern California, Department of Preventive Medicine"
output:
  html_document:
    css: styles.css
    toc: yes
    toc_depth: 2
    toc_float: yes
editor_options:
  chunk_output_type: console
---

<!--Initialize-->

``` {r setup, include=FALSE}

### Install necessary packages and get started
library(reshape2)
library(tidyverse)
library(ggplot2)
library(plotly)
library(ggrepel)
library(bindata)
library(odin)
library(fitR)
library(knitr)
library(EasyABC)
library(gridExtra)
library(odin)
library(lubridate)
library(EasyABC)
library(gridExtra)
library(kableExtra)
library(plyr)
library(dplyr)
library(data.table)
library(scales)
library(EasyABC)
library(patchwork)

library(tidyr)
library(readr)
library(purrr)
library(tibble)
library(stringr)
library(forcats)
library(network)
library(tidygraph)
library(ggraph)
library(visNetwork)
library(networkD3)
library(ggmosaic)
library(formattable)
library(DT)
library(reshape)
library(here)
library(fs)

library(MASS)
library(plotly)
library(fBasics)

lang_output <- function(x, lang) {
  cat(c(sprintf("```%s", lang), x, "```"), sep = "\n")
}
r_output <- function(x) lang_output(x, "r")

knitr::opts_chunk$set(
  fig.width = 9.5,
  fig.height = 8,
  eval=TRUE,
  echo=FALSE,
  warning=FALSE,
  cache=FALSE,
  message=FALSE,
  include=TRUE
  )

# code.dir=here("/Users/juliachen/Desktop/covid19/code/")
# data.dir=here("/Users/juliachen/Desktop/covid19/data/")
# result.dir = here("/Users/juliachen/Desktop/covid19/results/")
# fig.dir = here("/Users/juliachen/Desktop/covid19/figs/")
# output.dir = here("/Users/juliachen/Desktop/covid19/output/")
# code.paper.dir=here("/Users/juliachen/Desktop/covid19/code/epi_model_code")
# code.risk.dir=here("/Users/juliachen/Desktop/covid19/code/risk_model_code/")
# code.scenarios.dir=here("/Users/juliachen/Desktop/covid19/code/scenarios_code/")

code.dir=here("code/")
data.dir=here("data/")
result.dir = here("results/")
fig.dir = here("figs/")
output.dir = here("output/")
code.paper.dir=here("code/epi_model_code")
code.risk.dir=here("code/risk_model_code/")
code.scenarios.dir=here("code/scenarios_code/")

```

<!--Set global options-->

```{r options, include=FALSE}
print.output <- FALSE
days.truncate <- 0
endDatePlotGlobal <- as.Date("2021-03-16")
```


<!--Read in epidemic model, functions, COVID data-->

```{r read-in-model-supporting-functions, include=FALSE}

###################################################################################################
## LOAD EPIDEMIC MODEL
## And compile the model
path_seihqdr_model <- path(code.paper.dir, "stochastic_SEIAHQDR_Alphat_rt.R")
seihqdr_generator <- odin::odin(path_seihqdr_model)

###################################################################################################
## LOAD DATA PROCESSING AND MODEL ESTIMATING FUNCTIONS
## for week 1
model_functions_week1 <- path(code.paper.dir, "data_model_fun.R")
source(model_functions_week1)

###################################################################################################
## LOAD PLOTTING FUNCTIONS
plot_code <- path(code.paper.dir, "plotting_fun_NEW.R")
source(plot_code)

###################################################################################################
## LOAD TABLES FUNCTIONS
tables_code <- path(code.paper.dir, "tables_fun.R")
source(tables_code)

###################################################################################################
## COVID INPUT DATA
# latest_data: cumulative and daily counts for "Htotcum","D","Vcum","Idetectcum","H_new","D_new"
# no_obs: number of observation days
latest_data <- latest_covid_data(truncate=days.truncate)
no_obs <- nrow(latest_data)
```


<!--Model Fitting--> <!--Week1-->
```{r include=FALSE}
## SOURCE PRIOR PARAMETERS
## Provides output in form of a prior.par list
## Note: Beta(t), Alpha(t), Kappa(t), Delta(t) are read in from file

## LOAD DATA PROCESSING AND MODEL ESTIMATING FUNCTIONS
## for week 1
model_functions_week1 <- path(code.paper.dir, "data_model_fun_w1.R")
source(model_functions_week1)

prior_param_input_week1 <- path(code.paper.dir, "prior_param.R")
source(prior_param_input_week1)


## SUMMARY STATISTICS COMPUTED ON DATA
### Here we extract from the observed data exactly the same number of days of data as we extract from the model in the model.1sim.stats.no.R code
week.no = 1
summarydata <- sum.stats.SIMTEST(latest_data[c(1:(7*week.no+1)),])  
model.R <- model.1sim.stats.no.R  # From supporting_functions

### NUMBER OF OUTPUTS
n_calibration = 1000
n_rec = 100

## Week1 FIT MODEL
ABC_out<-ABC_mcmc(method="Marjoram",model=model.R,prior=prior.par,
                       summary_stat_target=summarydata, n_calibration=n_calibration,
                       tolerance_quantile=0.1,verbose=FALSE,progress=TRUE, n_rec=n_rec)

ABC.out.mat <- ABC_out$param
view(ABC.out.mat)
### Creat df for mean, sd and list for all parameters
week_par_mean = as.data.frame(matrix(0, ncol = 6, nrow = n_rec))
week_par_sd = as.data.frame(matrix(0, ncol = 6, nrow = n_rec))
week_par_all <- vector("list", nrow(ABC.out.mat))

ABC.par.out_week_1 <- as.data.frame(ABC_out$param)

week_par_mean[1,] = colMeans(ABC_out$param)
week_par_sd[1,] = colStdevs(ABC_out$param)
week_par_all[[1]] <- ABC.par.out_week_1
```


<!--Week2-->
```{r}
## Note: Beta(t), Alpha(t), Kappa(t), Delta(t) are read in from file
prior_param_input_week2 <- path(code.paper.dir, "prior_param_w2.R")
source(prior_param_input_week2)

## LOAD DATA PROCESSING AND MODEL ESTIMATING FUNCTIONS
## for week 1 later
model_functions_week2<- path(code.paper.dir, "data_model_fun_w2.R")
source(model_functions_week2)

## SUMMARY STATISTICS COMPUTED ON DATA
### Here we extract from the observed data exactly the same number of days of data as we extract from the model in the model.1sim.stats.no.R code
week.no = 2
summarydata <- sum.stats.SIMTEST(latest_data[c(1:(7*week.no+1)),])   
model.R <- model.1sim.stats.no.R  # From supporting_functions

## Week2 
ABC_out<-ABC_mcmc(method="Marjoram",model=model.R,prior=prior.par,
                       summary_stat_target=summarydata, n_calibration=n_calibration,
                       tolerance_quantile=0.1,verbose=FALSE,progress=TRUE, n_rec=n_rec)

ABC.out.mat <- ABC_out$param
view(ABC.out.mat)

ABC.par.out_week_2 <- as.data.frame(ABC_out$param)
## Here I'm ensuring we don't get any negative values for our parameters -- see how I specified in model.1sim.stats.no.R (in data_model_fun_w2.R) the maximum between each parameter and 0.01; in that way the ABC algorithm will implement that value in simulating the model, but the value it stores in ABC_out$param is the original one it chose (before the max(-,0.01) was applied). So we have to do an extra step here to ensure the saved values are the max(-, 0.01) ones. 
for (i in 1:nrow(ABC.par.out_week_2)){
  ABC.par.out_week_3$V2[i] <- max(ABC.par.out_week_3$V2[i] , .01)
  ABC.par.out_week_2$V3[i] <- max(ABC.par.out_week_2$V3[i] , .01)
  ABC.par.out_week_2$V4[i] <- max(ABC.par.out_week_2$V4[i] , .01)
  ABC.par.out_week_2$V5[i] <- max(ABC.par.out_week_2$V5[i] , .01)
  ABC.par.out_week_2$V6[i] <- max(ABC.par.out_week_2$V6[i] , .01)
}

week_par_mean[2,] = colMeans(ABC.par.out_week_2)
week_par_sd[2,] = colStdevs(ABC.par.out_week_2)
week_par_all[[2]] <- ABC.par.out_week_2
```


<!--Week3 and later later-->
```{r}
## Note: Beta(t), Alpha(t), Kappa(t), Delta(t) are read in from file
#prior_param_input_week3later <- path(code.paper.dir, "prior_param_w3later.R")
#source(prior_param_input_week3later)

## LOAD DATA PROCESSING AND MODEL ESTIMATING FUNCTIONS
#model_functions_week3later<- path(code.paper.dir, "data_model_fun_w3later.R")
#source(model_functions_week3later)

## SUMMARY STATISTICS COMPUTED ON DATA
week.no = c(5:10) #c(3:52)
week.no=Vectorize(week.no)

for (i in week.no){
  
  prior.R0 = c("normal", week_par_mean[i-1,1], week_par_sd[i-1,1])
  # r
  prior.r = c("normal", week_par_mean[i-1,2], week_par_sd[i-1,2])
  # Delta
  prior.Delta = c("normal", week_par_mean[i-1,3], week_par_sd[i-1,3])
  # Alpha 
  prior.Alpha = c("normal", week_par_mean[i-1,4], week_par_sd[i-1,4])
  # Kappa
  prior.Kappa = c("normal", week_par_mean[i-1,5], week_par_sd[i-1,5])
  # p_V
  prior.p_V = c("normal", week_par_mean[i-1,6], week_par_sd[i-1,6]) 
  
  prior.par <- list(
  prior.R0,
  prior.r,
  prior.Delta,
  prior.Alpha,
  prior.Kappa,
  prior.p_V)
  
  model_functions_week3later<- path(code.paper.dir, "data_model_fun_w3later.R")
  source(model_functions_week3later)
  
  
    summarydata <- sum.stats.SIMTEST(latest_data[c(1:(7*i+1)),])   
    model.R <- model.1sim.stats.no.R  # From supporting_functions

    ABC_out<-ABC_mcmc(method="Marjoram",model=model.R,prior=prior.par,
                       summary_stat_target=summarydata, n_calibration=n_calibration,
                       tolerance_quantile=0.1,verbose=FALSE,progress=TRUE, n_rec=n_rec)
    ABC.out.mat <- ABC_out$param
    ABC.par.out_week <- as.data.frame(ABC_out$param)
    
    for (j in 1:nrow(ABC.par.out_week)){
        ABC.par.out_week$V1[j] <- max(ABC.par.out_week$V1[j] , .01)
        ABC.par.out_week$V2[j] <- max(ABC.par.out_week$V2[j] , .01)
        ABC.par.out_week$V3[j] <- max(ABC.par.out_week$V3[j] , .01)
        ABC.par.out_week$V4[j] <- max(ABC.par.out_week$V4[j] , .01)
        ABC.par.out_week$V5[j] <- max(ABC.par.out_week$V5[j] , .01)
        ABC.par.out_week$V6[j] <- max(ABC.par.out_week$V6[j] , .01)
    }
    week_par_mean[i,] = colMeans(ABC.par.out_week)
    week_par_sd[i,] = colStdevs(ABC.par.out_week)
    week_par_all[[i]] <- ABC.par.out_week
}
```



<!--Simulate model-->
<!--Get compartment variables over time with CI-->
<!--Get CFR/IFR-->

```{r include=FALSE}
###################################################################################################
## GET MODEL OUTPUT: traj.0

ABC.out.mat <- ABC_out$param
par.vec.length <- nrow(ABC_out$param)
iter <- 10
time.steps <- 400
vars.to.plot <- vars.plus.R

## FUNCTION MODEL.OUTPUT.TO.PLOT.SIM
## Calculates mean and CI of each estimated parameter & CFR/IFR
## Uses correlated.param.SIM
## Reads in Beta, Alpha, Kappa, Delta from file
traj.0 <- model.output.to.plot.SIM(ABC.out.mat=ABC.out.mat, par.vec.length=par.vec.length, iter=iter, time.steps=time.steps, vars.to.plot = vars.to.plot)

```


```{r include=FALSE}

###################################################################################################
## Plot all variables current date

time.steps.4.plot = endDatePlotGlobal - as.Date("2020-03-01")
data.in <- latest_data
vars.to.plot <- vars.plus.R

plot.all.variables.curr.date <- 
plot.model.data.all(traj.CI = traj.0, data.in = data.in, init.date.data = "2020-03-01", date.offset.4plot = 0, time.steps.4plot=time.steps.4.plot,
                    vars.to.plot=vars.plus.R)

if (print.output==TRUE){
  pdf(file = path(output.dir, "plot.all.variables.pdf"), width=10, height =10)
  plot.all.variables.curr.date
  dev.off()
}
plot.all.variables.curr.date

```


```{r include=FALSE}
time.steps.4plot = endDatePlotGlobal - as.Date("2020-03-01")
data.in <- latest_data
plot.annotations <- TRUE
plot.capacity <- TRUE
ymax=NULL

## OBSERVED ONLY
var.to.plot <- "I"
plot.percent.OBS <- plot.percent.LAC(traj.CI=traj.0, data.in=data.in, init.date.data=as.Date("2020-03-01"), time.steps.4plot=time.steps.4plot, ymax=NULL, plot.capacity=NULL, plot.annotations=TRUE, var.to.plot=var.to.plot)

date.selected <- Sys.Date()
var.to.plot <- "I"
percent.current.OBS <- get.current.percent(traj.CI=traj.0, date.selected=date.selected,var.to.plot = var.to.plot)

date.selected <- Sys.Date()+10
var.to.plot <- "I"
percent.in10days.OBS <- get.current.percent(traj.CI=traj.0, date.selected=date.selected,var.to.plot = var.to.plot)


## OBSERVED AND UNOBSERVED 
var.to.plot <- "Itot"
plot.percent.TOT <- plot.percent.LAC(traj.CI=traj.0, data.in=data.in, init.date.data=as.Date("2020-03-01"), time.steps.4plot=time.steps.4plot, ymax=NULL, plot.capacity=NULL, plot.annotations=TRUE, var.to.plot=var.to.plot)

date.selected <- Sys.Date()
var.to.plot <- "Itot"
percent.current.TOT <- get.current.percent(traj.CI=traj.0, date.selected=date.selected,var.to.plot = var.to.plot)

date.selected <- Sys.Date()+10
var.to.plot <- "Itot"
percent.in10days.TOT <- get.current.percent(traj.CI=traj.0, date.selected=date.selected,var.to.plot = var.to.plot)


```

## Percentage of LAC population currently infected 

### % LAC population currently infected: observed + estimated unobserved infections

* **The percentage infected on `r Sys.Date()` is estimated at `r percent.current.TOT`.**

* **The percentage infected on `r date.selected`, *under the assumption of the infectious rate as of `r Sys.Date()`*, is estimated at `r percent.in10days.TOT`.**

This plot shows the model-estimated total percentage (%) of the LAC population infected, accounting for **both observed and unobserved cases**.

```{r}
ggplotly(plot.percent.TOT)
```

### % LAC population currently infected: observed infections only

* **The percentage infected on `r Sys.Date()` is estimated at `r percent.current.OBS`.**

* **The percentage infected on `r date.selected`, *under the assumption of the infectious rate as of `r Sys.Date()`*, is estimated at `r percent.in10days.OBS`.**

This plot shows the model-estimated total percentage (%) of the LAC population infected, accounting only for **confirmed observed cases**.

```{r}
ggplotly(plot.percent.OBS)
```



## Estimated epidemic parameters {.tabset}

```{r include=FALSE}

endDatePlot <- endDatePlotGlobal
Fig3.plots <- plot.param.t(ABC_out = ABC_out, endDatePlot=endDatePlot)

if (print.output==TRUE){
  pdf(file = path(output.dir, "plot_Rt.pdf"), width=10, height =10)
  Fig3.plots[[1]]
  dev.off()
  
  pdf(file = path(output.dir, "plot_r_t.pdf"), width=10, height =10)
  Fig3.plots[[2]]
  dev.off()
  
  pdf(file = path(output.dir, "plot_AKD_t.pdf"), width=10, height =10)
  Fig3.plots[[3]]
  dev.off()
}

```

### Reproductive Number, $R(t)$

This plot shows the time-varying Effective Reproductive Number R(t). This accounts for the fraction of the population that is assumed to be immune to reinfection through infection-acquired immunity. It does not account for the fraction of the population that has been vaccinated, although this is currently very small and would not make a sizeable impact.

```{r}
R_t_plot <- Fig3.plots[[1]]
ggplotly(R_t_plot)
```

### Fraction of Observed Infections, $r(t)$

```{r}
Fig3.plots[[2]]
```

{-}


<!---
Single compartment plots
--->

```{r include=FALSE}

time.steps.4.plot = endDatePlotGlobal - as.Date("2020-03-01") + 1
data.in <- latest_data
plot.annotations <- TRUE
plot.capacity <- TRUE
ymax=NULL

## Get compartmental variable plots TOGETHER and print/save
plot.out.H.I <- plot.out.compartmental(traj.CI = traj.CI, endDatePlot = endDatePlot)

if (print.output==TRUE){
  pdf(file = path(output.dir, "curr_infect_TOGETHER.pdf"), width=10, height =10)
  plot.out.H.I[[2]]
  dev.off()
  
  pdf(file = path(output.dir, "curr_healthcare_TOGETHER.pdf"), width=10, height =10)
  plot.out.H.I[[1]]
  dev.off()
}

## Get plots for individual variables (for ggplotly)

var.to.plot <- "I_detect_new"
#ymax=60000
plot.I.new <- plot.model.single(traj.CI=traj.0, data.in=data.in, init.date.data="2020-03-01",time.steps.4plot=time.steps.4plot, 
                                ymax=ymax, plot.capacity=plot.capacity, plot.annotations=plot.annotations, var.to.plot=var.to.plot)

var.to.plot <- "I"
#ymax=60000
plot.I <- plot.model.single(traj.CI=traj.0, data.in=data.in, init.date.data="2020-03-01",time.steps.4plot=time.steps.4plot, 
                                ymax=ymax, plot.capacity=plot.capacity, plot.annotations=plot.annotations, var.to.plot=var.to.plot)

var.to.plot <- "Itot"
#ymax=200000
plot.Itot <- plot.model.single(traj.CI=traj.0, data.in=data.in, init.date.data="2020-03-01",time.steps.4plot=time.steps.4plot, 
                                ymax=ymax, plot.capacity=plot.capacity, plot.annotations=plot.annotations, var.to.plot=var.to.plot)

var.to.plot <- "Itotcum"
#ymax=200000
plot.Itotcum <- plot.model.single(traj.CI=traj.0, data.in=data.in, init.date.data="2020-03-01",time.steps.4plot=time.steps.4plot, 
                                ymax=ymax, plot.capacity=plot.capacity, plot.annotations=plot.annotations, var.to.plot=var.to.plot)
ggplotly(plot.Itotcum)

var.to.plot <- "Htot"
#ymax = 3000
plot.Htot <- plot.model.single(traj.CI=traj.0, data.in=data.in, init.date.data="2020-03-01",time.steps.4plot=time.steps.4plot, 
                                ymax=ymax, plot.capacity=plot.capacity, plot.annotations=plot.annotations, var.to.plot=var.to.plot)

var.to.plot <- "Q"
#ymax = 3000
plot.Q <- plot.model.single(traj.CI=traj.0, data.in=data.in, init.date.data="2020-03-01",time.steps.4plot=time.steps.4plot, 
                                ymax=ymax, plot.capacity=plot.capacity, plot.annotations=plot.annotations, var.to.plot=var.to.plot)


var.to.plot <- "D_new"
#ymax = 200
plot.Dnew <- plot.model.single(traj.CI=traj.0, data.in=data.in, init.date.data="2020-03-01",time.steps.4plot=time.steps.4plot, 
                                ymax=ymax, plot.capacity=plot.capacity, plot.annotations=plot.annotations, var.to.plot=var.to.plot)
```

## Numbers infected {.tabset}

* **New = new daily incidence**
* **Current = current census in compartment** 
* **Cumulative = running total over time**
* Black dots depict COVID-19 data

### Current estimated total infections

```{r width=3}
ggplotly(plot.Itot)
```

### Current observed infections

```{r}
ggplotly(plot.I)
```

### New observed infections (with data)

```{r}
ggplotly(plot.I.new)
```

### Current observed and total infections (together)

```{r}
plot.out.H.I[[2]]
```

{-}

## Numbers of Hospitalizations, ICU admissions, Deaths {.tabset}

* **New = new daily incidence**
* **Current = current census in compartment** 
* **Cumulative = running total over time**
* Black dots depict COVID-19 data
* Dotted black line marks healthcare capacity limits

### Current in hospital

```{r}
ggplotly(plot.Htot)
```

### Current in ICU

```{r}
ggplotly(plot.Q)
```

### New deaths

```{r}
ggplotly(plot.Dnew)
```

### Current hospitalizations, ventilations, and new deaths

```{r}
plot.out.H.I[[1]]
```

### Probabilities of severe illness

- Probability of hospitalization given infection, $\alpha(t)$

- Probability of ICU admission given hospitalization, $\kappa(t)$

- Probability of death given ICU admission, $\delta(t)$

```{r}
Fig3.plots[[3]]
```

## Model fits {.tabset}

Summarizes the epidemic model fit with COVID-19 data for LAC from March 1 through `r as.Date("2020-03-01") + no_obs` for all disease states across multiple views: New cases, representing new daily incidence; the current number in a compartment at a specific date, relevant for understanding current prevalence rates and comparing with healthcare capacity limitations; and cumulative counts until a specific date. Observed data for available compartments with cases attributable to nursing home residents removed, are plotted as black dots. The figure demonstrates that good model fits are achieved in all compartments across time.

* **New = new daily incidence**
* **Current = current census in compartment** 
* **Cumulative = running total over time**
* Black dots depict COVID-19 data, with counts from outbreaks in nursing homes removed
* The dashed line represents healthcare resource capacity limits

```{r include=FALSE}

###################################################################################################
## Plot all variables current date

time.steps.4.plot = Sys.Date() - as.Date("2020-03-01") +1
data.in <- latest_data
vars.to.plot <- vars.plus.R

plot.all.variables.curr.date <- 
plot.model.data.all(traj.CI = traj.0, data.in = data.in, init.date.data = "2020-03-01", date.offset.4plot = 0, time.steps.4plot=time.steps.4.plot,
                    vars.to.plot=vars.plus.R)

if (print.output==TRUE){
  pdf(file = path(output.dir, "plot.all.variables.pdf"), width=10, height =10)
  plot.all.variables.curr.date
  dev.off()
}
#plot.all.variables.curr.date

```

```{r include=FALSE}

###################################################################################################
## Plot all variables plus 15 days

time.steps.4.plot = endDatePlotGlobal - as.Date("2020-03-01") + 15
data.in <- latest_data
vars.to.plot <- vars.plus.R

plot.all.variables.plus.15.days <- 
plot.model.data.all(traj.CI = traj.0, data.in = data.in, init.date.data = "2020-03-01", date.offset.4plot = 0, time.steps.4plot=time.steps.4.plot,
                    vars.to.plot=vars.plus.R)

if (print.output==TRUE){
  pdf(file = path(output.dir, "plot.all.variables.pdf"), width=10, height =10)
  plot.all.variables.plus.15.days
  dev.off()
}
#plot.all.variables.plus.15.days
```

### Model fits through `r Sys.Date()`

```{r}
plot.all.variables.curr.date
```

### Model **projections** through `r date.selected`

Projections **under the assumption of the infectious rate as of `r Sys.Date()`** 

```{r}
plot.all.variables.plus.15.days
```


## Tables: Parameter estimates {.tabset}

```{r include=FALSE}
###################################################################################################
## GET MODEL OUTPUT: summary

startDatePlot <- as.Date("2020-03-01")
endDatePlot <- endDatePlotGlobal
all_day_1s <- seq(startDatePlot,endDatePlot,by='month')
all_day_15s <- all_day_1s+14
date.in <- sort(c(all_day_1s,all_day_15s))
tables.out <- summary.table.param.CFR.IFR(traj.CI=traj.0, ABC_out=ABC_out, date.in=date.in, use.mean.select = 1, round.by.in=4)

```

### $R0$, $r(t)$, $\mu(t)$
```{r}
formattable(tables.out[[1]])
if (print.output==TRUE) write.csv(tables.out[[1]], file = path(output.dir, "R.r.mu_table.csv"))
```

### Probabilities of severe illness

- Probability of hospitalization given infection, $\alpha(t)$

- Probability of ICU admission given hospitalization, $\kappa(t)$

- Probability of death given ICU admission, $\delta(t)$

```{r}
formattable(tables.out[[2]])
akd_table <- tables.out[[2]]
if (print.output==TRUE) write.csv(tables.out[[2]], file = path(output.dir, "AKD_t_table.csv"))
```

### CFR and IFR

```{r}
formattable(tables.out[[3]])
if (print.output==TRUE) write.csv(tables.out[[3]], file = path(output.dir, "CFR_IFR_table.csv"))
```


## Figures: CFR and IFR

```{r include=FALSE}

startDatePlot <- as.Date("2020-03-01")
endDatePlot <- endDatePlotGlobal #as.Date("2021-02-01")
all_day_1s <- seq(startDatePlot,endDatePlot,by='month')
all_day_15s <- all_day_1s+14
date.in <- sort(c(all_day_1s,all_day_15s))

CFR.IFR.plots.out <- CFR.IFR.plots(traj.CI=traj.0, date.in=date.in, endDatePlot = endDatePlot)

if (print.output==TRUE){
  pdf(file = path(output.dir, "CFR_plot.pdf"), width=10, height =10)
  CFR.IFR.plots.out[[1]]
  dev.off()
  
  pdf(file = path(output.dir, "IFR_plot.pdf"), width=10, height =10)
  CFR.IFR.plots.out[[2]]
  dev.off()
}
```

### Time-varying CFR(t)

```{r}
CFR.IFR.plots.out[[1]]
```

### Time-varying IFR(t)
```{r}
CFR.IFR.plots.out[[2]]
```





