---
title: "COVID19 Modeling for Los Angeles County"
author: "University of Southern California, Department of Preventive Medicine"
output:
  pdf_document:
    toc: yes
    toc_depth: '2'
  html_document:
    css: styles.css
    toc: yes
    toc_depth: 2
    toc_float: yes
subtitle: Analysis updated with data as of December 6, 2020
editor_options:
  chunk_output_type: console
---

<!--Initialize-->

``` {r setup, include=FALSE}

### Install necessary packages and get started

library(reshape2)
library(tidyverse)
library(ggplot2)
library(plotly)
library(ggrepel)
library(bindata)
library(odin)
library(fitR)
library(knitr)
library(EasyABC)
library(gridExtra)
library(odin)
library(lubridate)
library(EasyABC)
library(gridExtra)
library(kableExtra)
library(plyr)
library(dplyr)
library(data.table)
library(scales)
library(EasyABC)
library(patchwork)

library(tidyr)
library(readr)
library(purrr)
library(tibble)
library(stringr)
library(forcats)
library(network)
library(tidygraph)
library(ggraph)
library(visNetwork)
library(networkD3)
library(ggmosaic)
library(formattable)
library(DT)
library(reshape)
library(here)
library(fs)

library(MASS)
library(plotly)

lang_output <- function(x, lang) {
  cat(c(sprintf("```%s", lang), x, "```"), sep = "\n")
}
r_output <- function(x) lang_output(x, "r")

knitr::opts_chunk$set(
  fig.width = 9.5,
  fig.height = 8,
  eval=TRUE,
  echo=FALSE,
  warning=FALSE,
  cache=FALSE,
  message=FALSE,
  include=TRUE
  )

code.dir=here("code/")
data.dir=here("data/")
result.dir = here("results/")
fig.dir = here("figs/")
output.dir = here("output/")
code.paper.dir=here("code/epi_model_code")
code.risk.dir=here("code/risk_model_code/")
code.scenarios.dir=here("code/scenarios_code/")
```

<!--Set global options-->

```{r options, include=FALSE}
print.output <- FALSE
days.truncate <- 0
endDatePlot <- as.Date("2020-12-15")
```


<!--Read in epidemic model, functions, COVID data-->

```{r read-in-model-supporting-functions, include=FALSE}

###################################################################################################
## LOAD EPIDEMIC MODEL
## And compile the model
path_seihqdr_model <- path(code.paper.dir, "stochastic_SEIAHQDR_Alphat_rt.R")
seihqdr_generator <- odin::odin(path_seihqdr_model)

###################################################################################################
## LOAD DATA PROCESSING AND MODEL ESTIMATING FUNCTIONS
model_functions <- path(code.paper.dir, "data_model_fun.R")
source(model_functions)

###################################################################################################
## LOAD PLOTTING FUNCTIONS
plot_code <- path(code.paper.dir, "plotting_fun_NEW.R")
source(plot_code)

###################################################################################################
## LOAD TABLES FUNCTIONS
tables_code <- path(code.paper.dir, "tables_fun.R")
source(tables_code)

###################################################################################################
## COVID INPUT DATA
# latest_data: cumulative and daily counts for "Htotcum","D","Vcum","Idetectcum","H_new","D_new"
# no_obs: number of observation days
latest_data <- latest_covid_data(truncate=days.truncate)
no_obs <- nrow(latest_data)

```


<!--Model Fitting-->

```{r include=FALSE}

## SOURCE PRIOR PARAMETERS
## Provides output in form of a prior.par list
## Note: Beta(t), Alpha(t), Kappa(t), Delta(t) are read in from file
prior_param_input <- path(code.paper.dir, "prior_param.R")
source(prior_param_input)
# prior.par

## SUMMARY STATISTICS COMPUTED ON DATA
summarydata <- sum.stats.SIMTEST(latest_data,include.R = FALSE)
model.R <- model.1sim.stats.no.R  # From supporting_functions

### NUMBER OF OUTPUTS
# n_calibration = 10000
# n_rec = 2000

n_calibration = 1000
n_rec = 100

## FIT MODEL
ABC_out<-ABC_mcmc(method="Marjoram",model=model.R,prior=prior.par,
                       summary_stat_target=summarydata, n_calibration=n_calibration,
                       tolerance_quantile=0.1,verbose=FALSE,progress=TRUE, n_rec=n_rec)

ABC.par.out <- as.data.frame(ABC_out$param)
ABC.out.mat <- ABC_out$param
par.vec.length <- nrow(ABC_out$param)

```


<!--Simulate model-->
<!--Get compartment variables over time with CI-->
<!--Get CFR/IFR-->

```{r include=FALSE}
###################################################################################################
## GET MODEL OUTPUT: traj.0

ABC.out.mat <- ABC_out$param
par.vec.length <- nrow(ABC_out$param)
iter <- 10
time.steps <- 400
vars.to.plot <- vars.plus.R

## FUNCTION MODEL.OUTPUT.TO.PLOT.SIM
## Calculates mean and CI of each estimated parameter & CFR/IFR
## Uses correlated.param.SIM
## Reads in Beta, Alpha, Kappa, Delta from file
traj.0 <- model.output.to.plot.SIM(ABC.out.mat=ABC.out.mat, par.vec.length=par.vec.length, iter=iter, time.steps=time.steps, vars.to.plot = vars.to.plot)

```


```{r include=FALSE}

###################################################################################################
## Plot all variables current date

time.steps.4.plot = as.Date("2020-12-15") - as.Date("2020-03-01") +1
data.in <- latest_data
vars.to.plot <- vars.plus.R

plot.all.variables.curr.date <- 
plot.model.data.all(traj.CI = traj.0, data.in = data.in, init.date.data = "2020-03-01", date.offset.4plot = 0, time.steps.4plot=time.steps.4.plot,
                    vars.to.plot=vars.plus.R)

if (print.output==TRUE){
  pdf(file = path(output.dir, "plot.all.variables.pdf"), width=10, height =10)
  plot.all.variables.curr.date
  dev.off()
}
plot.all.variables.curr.date

```

# Epidemic model

```{r include=FALSE}
time.steps.4plot = as.Date("2020-12-15") - as.Date("2020-03-01")
data.in <- latest_data
plot.annotations <- TRUE
plot.capacity <- TRUE
ymax=NULL

var.to.plot <- "I"
plot.percent.OBS <- plot.percent.LAC(traj.CI=traj.0, data.in=data.in, init.date.data=as.Date("2020-03-01"), time.steps.4plot=time.steps.4plot, ymax=NULL, plot.capacity=NULL, plot.annotations=TRUE, var.to.plot=var.to.plot)

var.to.plot <- "Itot"
plot.percent.TOT <- plot.percent.LAC(traj.CI=traj.0, data.in=data.in, init.date.data=as.Date("2020-03-01"), time.steps.4plot=time.steps.4plot, ymax=NULL, plot.capacity=NULL, plot.annotations=TRUE, var.to.plot=var.to.plot)

date.selected <- "2020-12-09"
var.to.plot <- "Itot"
percent.12.09 <- get.current.percent(traj.CI=traj.0, date.selected=date.selected,var.to.plot = var.to.plot)

date.selected <- "2020-12-20"
var.to.plot <- "Itot"
percent.12.20 <- get.current.percent(traj.CI=traj.0, date.selected=date.selected,var.to.plot = var.to.plot)


```

# Percentage of LAC population currently infected {.tabset}

The percentage infected on 12-09-2020 is estimated at `r percent.12.09`.

The percentage infected on 12-20-2020, under the assumption of the infectious rate as of 12-09-2020, is estimated at `r percent.12.20`.

### % LAC population currently infected: total infections

This plot shows the model-estimated total percentage (%) of the LAC population infected, including observed and estimated unobserved cases.

```{r}
ggplotly(plot.percent.TOT)
```

### Model-estimated total % LAC population currently infected

This plot shows the model-estimated percentage (%) of the LAC population infected, including only observed cases.

```{r}
ggplotly(plot.percent.OBS)
```

<!---
Single compartment plots
--->

```{r include=FALSE}

time.steps.4.plot = as.Date("2020-12-15") - as.Date("2020-03-01") + 1
data.in <- latest_data
plot.annotations <- TRUE
plot.capacity <- TRUE
ymax=NULL

## Get compartmental variable plots TOGETHER and print/save
plot.out.H.I <- plot.out.compartmental(traj.CI = traj.CI, endDatePlot = endDatePlot)

if (print.output==TRUE){
  pdf(file = path(output.dir, "curr_infect_TOGETHER.pdf"), width=10, height =10)
  plot.out.H.I[[2]]
  dev.off()
  
  pdf(file = path(output.dir, "curr_healthcare_TOGETHER.pdf"), width=10, height =10)
  plot.out.H.I[[1]]
  dev.off()
}

## Get plots for individual variables (for ggplotly)

var.to.plot <- "I_detect_new"
#ymax=60000
plot.I.new <- plot.model.single(traj.CI=traj.0, data.in=data.in, init.date.data="2020-03-01",time.steps.4plot=time.steps.4plot, 
                                ymax=ymax, plot.capacity=plot.capacity, plot.annotations=plot.annotations, var.to.plot=var.to.plot)

var.to.plot <- "I"
#ymax=60000
plot.I <- plot.model.single(traj.CI=traj.0, data.in=data.in, init.date.data="2020-03-01",time.steps.4plot=time.steps.4plot, 
                                ymax=ymax, plot.capacity=plot.capacity, plot.annotations=plot.annotations, var.to.plot=var.to.plot)

var.to.plot <- "Itot"
#ymax=200000
plot.Itot <- plot.model.single(traj.CI=traj.0, data.in=data.in, init.date.data="2020-03-01",time.steps.4plot=time.steps.4plot, 
                                ymax=ymax, plot.capacity=plot.capacity, plot.annotations=plot.annotations, var.to.plot=var.to.plot)

var.to.plot <- "Htot"
#ymax = 3000
plot.Htot <- plot.model.single(traj.CI=traj.0, data.in=data.in, init.date.data="2020-03-01",time.steps.4plot=time.steps.4plot, 
                                ymax=ymax, plot.capacity=plot.capacity, plot.annotations=plot.annotations, var.to.plot=var.to.plot)

var.to.plot <- "Q"
#ymax = 3000
plot.Q <- plot.model.single(traj.CI=traj.0, data.in=data.in, init.date.data="2020-03-01",time.steps.4plot=time.steps.4plot, 
                                ymax=ymax, plot.capacity=plot.capacity, plot.annotations=plot.annotations, var.to.plot=var.to.plot)


var.to.plot <- "D_new"
#ymax = 200
plot.Dnew <- plot.model.single(traj.CI=traj.0, data.in=data.in, init.date.data="2020-03-01",time.steps.4plot=time.steps.4plot, 
                                ymax=ymax, plot.capacity=plot.capacity, plot.annotations=plot.annotations, var.to.plot=var.to.plot)
```

## Figures: Infections {.tabset}

* **New = new daily incidence**
* **Current = current census in compartment** 
* **Cumulative = running total over time**
* Black dots depict COVID-19 data

### Current estimated total infections

```{r width=3}
ggplotly(plot.Itot)
```

### Current observed infections

```{r}
ggplotly(plot.I)
```

### New observed infections (with data)

```{r}
ggplotly(plot.I.new)
```

### Current observed and total infections (together)

```{r}
plot.out.H.I[[2]]
```

{-}

## Figures: Reproductive number and fraction of infections detected {.tabset}

```{r include=FALSE}

#endDatePlot <- as.Date("2020-12-01")
Fig3.plots <- plot.param.t(ABC_out = ABC_out, endDatePlot=endDatePlot)

if (print.output==TRUE){
  pdf(file = path(output.dir, "plot_Rt.pdf"), width=10, height =10)
  Fig3.plots[[1]]
  dev.off()
  
  pdf(file = path(output.dir, "plot_r_t.pdf"), width=10, height =10)
  Fig3.plots[[2]]
  dev.off()
  
  pdf(file = path(output.dir, "plot_AKD_t.pdf"), width=10, height =10)
  Fig3.plots[[3]]
  dev.off()
}

```

### Reproductive Number, $R(t)$

```{r}
Fig3.plots[[1]]
```

### Fraction of Observed Infections, $r(t)$

```{r}
Fig3.plots[[2]]
```

{-}

## Figures: Hospitalizations, ICU admissions, deaths {.tabset}

* **New = new daily incidence**
* **Current = current census in compartment** 
* **Cumulative = running total over time**
* Black dots depict COVID-19 data
* Dotted black line marks healthcare capacity limits

### Current in hospital

```{r}
ggplotly(plot.Htot)
```

### Current in ICU

```{r}
ggplotly(plot.Q)
```

### New deaths

```{r}
ggplotly(plot.Dnew)
```

### Current hospitalizations, ventilations, and new deaths

```{r}
plot.out.H.I[[1]]
```

### $\alpha(t)$, $\kappa(t)$, $\delta(t)$

Probability of hospitalization given infection, $\alpha(t)$
Probability of ICU admission given hospitalization, $\kappa(t)$
Probability of death given ICU admission, $\delta(t)$

```{r}
Fig3.plots[[3]]
```

## Figures: Model fits {.tabset}

Summarizes the epidemic model fit with COVID-19 data for LAC from March 1 through `r as.Date("2020-03-01") + no_obs` for all disease states across multiple views: New cases, representing new daily incidence; the current number in a compartment at a specific date, relevant for understanding current prevalence rates and comparing with healthcare capacity limitations; and cumulative counts until a specific date. Observed data for available compartments with cases attributable to nursing home residents removed, are plotted as black dots. The figure demonstrates that good model fits are achieved in all compartments across time.

* **New = new daily incidence**
* **Current = current census in compartment** 
* **Cumulative = running total over time**
* Black dots depict COVID-19 data, with counts from outbreaks in nursing homes removed
* The dashed line represents healthcare resource capacity limits

```{r include=FALSE}

###################################################################################################
## Plot all variables current date

time.steps.4.plot = as.Date("2020-12-15") - as.Date("2020-03-01") +1
data.in <- latest_data
vars.to.plot <- vars.plus.R

plot.all.variables.curr.date <- 
plot.model.data.all(traj.CI = traj.0, data.in = data.in, init.date.data = "2020-03-01", date.offset.4plot = 0, time.steps.4plot=time.steps.4.plot,
                    vars.to.plot=vars.plus.R)

if (print.output==TRUE){
  pdf(file = path(output.dir, "plot.all.variables.pdf"), width=10, height =10)
  plot.all.variables.curr.date
  dev.off()
}
#plot.all.variables.curr.date

```

```{r include=FALSE}

###################################################################################################
## Plot all variables plus 15 days

time.steps.4.plot = as.Date("2020-12-15") - as.Date("2020-03-01") + 15
data.in <- latest_data
vars.to.plot <- vars.plus.R

plot.all.variables.plus.15.days <- 
plot.model.data.all(traj.CI = traj.0, data.in = data.in, init.date.data = "2020-03-01", date.offset.4plot = 0, time.steps.4plot=time.steps.4.plot,
                    vars.to.plot=vars.plus.R)

if (print.output==TRUE){
  pdf(file = path(output.dir, "plot.all.variables.pdf"), width=10, height =10)
  plot.all.variables.plus.15.days
  dev.off()
}
#plot.all.variables.plus.15.days
```

### Model fits through December 6th

```{r}
plot.all.variables.curr.date
```

### Model projections through December 20th

```{r}
plot.all.variables.plus.15.days
```


## Tables: Parameter estimates {.tabset}

```{r include=FALSE}
###################################################################################################
## GET MODEL OUTPUT: summary

startDatePlot <- as.Date("2020-03-01")
endDatePlot <- as.Date("2020-12-15")
all_day_1s <- seq(startDatePlot,endDatePlot,by='month')
all_day_15s <- all_day_1s+14
date.in <- sort(c(all_day_1s,all_day_15s))
tables.out <- summary.table.param.CFR.IFR(traj.CI=traj.0, ABC_out=ABC_out, date.in=date.in, use.mean.select = 1, round.by.in=4)

```

### $R0$, $r(t)$, $\mu(t)$
```{r}
formattable(tables.out[[1]])
if (print.output==TRUE) write.csv(tables.out[[1]], file = path(output.dir, "R.r.mu_table.csv"))
```

### $\alpha(t)$, $\kappa(t)$, $\delta(t)$

```{r}
formattable(tables.out[[2]])
akd_table <- tables.out[[2]]
if (print.output==TRUE) write.csv(tables.out[[2]], file = path(output.dir, "AKD_t_table.csv"))
```

### CFR and IFR

```{r}
formattable(tables.out[[3]])
if (print.output==TRUE) write.csv(tables.out[[3]], file = path(output.dir, "CFR_IFR_table.csv"))
```


<!--CFR and IFR-->

```{r include=FALSE}

startDatePlot <- as.Date("2020-03-01")
endDatePlot <- as.Date("2020-12-31") #as.Date("2021-02-01")
all_day_1s <- seq(startDatePlot,endDatePlot,by='month')
all_day_15s <- all_day_1s+14
date.in <- sort(c(all_day_1s,all_day_15s))

CFR.IFR.plots.out <- CFR.IFR.plots(traj.CI=traj.0, date.in=date.in, endDatePlot = endDatePlot)

if (print.output==TRUE){
  pdf(file = path(output.dir, "CFR_plot.pdf"), width=10, height =10)
  CFR.IFR.plots.out[[1]]
  dev.off()
  
  pdf(file = path(output.dir, "IFR_plot.pdf"), width=10, height =10)
  CFR.IFR.plots.out[[2]]
  dev.off()
}
```

### Time-varying CFR(t)

```{r}
CFR.IFR.plots.out[[1]]
```

### Time-varying IFR(t)
```{r}
CFR.IFR.plots.out[[2]]
```





