---
title: "USC Predict COVID Project"
subtitle: "Predictive Epidemic Model for COVID-19 in Los Angeles County"
author: "University of Southern California, Department of Preventive Medicine"
output:
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
editor_options: 
  chunk_output_type: console
---

<!--Initialize-->

``` {r setup, include=FALSE}

### Install necessary packages and get started

library(reshape2)
library(tidyverse)
library(ggplot2)
library(plotly)
library(ggrepel)
library(bindata)
library(odin)
library(fitR)
library(knitr)
library(EasyABC)
library(gridExtra)
library(odin)
library(lubridate)
library(EasyABC)
library(gridExtra)
library(kableExtra)
library(plyr)
library(dplyr)
library(data.table)
library(scales)
library(EasyABC)
library(patchwork)

library(tidyr)
library(readr)
library(purrr)
library(tibble)
library(stringr)
library(forcats)
library(network)
library(tidygraph)
library(ggraph)
library(visNetwork)
library(networkD3)
library(ggmosaic)
library(formattable)
library(DT)
library(reshape)
library(here)
library(fs)

library(MASS)
library(plotly)

lang_output <- function(x, lang) {
  cat(c(sprintf("```%s", lang), x, "```"), sep = "\n")
}
r_output <- function(x) lang_output(x, "r")

knitr::opts_chunk$set(
  fig.width = 9.5,
  fig.height = 8,
  eval=TRUE,
  echo=FALSE,
  warning=FALSE,
  cache=FALSE,
  message=FALSE,
  include=TRUE
  )

code.dir=here("code/")
data.dir=here("data/")
result.dir = here("results/")
fig.dir = here("figs/")
output.dir = here("output/")
code.paper.dir=here("code/code_paper")

```

<!--Read in epidemic model, functions, COVID data-->

```{r read-in-model-supporting-functions, include=FALSE}

###################################################################################################
## LOAD EPIDEMIC MODEL
## And compile the model
path_seihqdr_model <- path(code.paper.dir, "stochastic_SEIAHQDR_Alphat_rt.R")
seihqdr_generator <- odin::odin(path_seihqdr_model)

###################################################################################################
## LOAD SUPPORTING FUNCTIONS
supporting_functions <- path(code.paper.dir, "supporting_fns_Alpha_t_paper_FULL.R")
r_output(tail(readLines(supporting_functions)))
source(supporting_functions)

# FUNCTIONS INCLUDED:
## READING IN LATEST LA COUNTY COVID DATA
## ABC
### sum.stats: A function specifying the data to COVID-19 data to fit the model to
### model.1sim.stats: A function implementing the model to be simulated
## PLOTTING
### correlated.param: SPECIFYING EPIDEMIC MODEL TO BE SIMULATED AND SCENARIOS
### model.output.to.plot: ETTING MODEL OUTPUT + SUMMARY STATISTICS FUNCTION
## SUMMARY TABLE GENERATING FUNCTIONS

###################################################################################################
## COVID INPUT DATA
# latest_data: cumulative and daily counts for "Htotcum","D","Vcum","Idetectcum","H_new","D_new"
# no_obs: number of observation days
latest_data <- latest_covid_data()
no_obs <- nrow(latest_data)

```


<!--Model Fitting-->

```{r include=FALSE}

## SOURCE PRIOR PARAMETERS
## Provides output in form of a prior.par list
## Note: Beta(t), Alpha(t), Kappa(t), Delta(t) are read in from file
prior_param_input <- path(code.paper.dir, "prior_param.R")
source(prior_param_input)
# prior.par

## SUMMARY STATISTICS COMPUTED ON DATA
summarydata <- sum.stats.SIMTEST(latest_data,include.R = FALSE)
model.R <- model.1sim.stats.no.R  # From supporting_functions

### FOR QUICK TESTS
n_calibration = 1000
n_rec = 100

### FOR LONGER TESTS
# n_calibration = 10000
# n_rec = 1000

## FIT MODEL
ABC_out<-ABC_mcmc(method="Marjoram",model=model.R,prior=prior.par,
                       summary_stat_target=summarydata, n_calibration=n_calibration,
                       tolerance_quantile=0.1,verbose=TRUE,progress=TRUE, n_rec=n_rec)

ABC.par.out <- as.data.frame(ABC_out$param)
ABC.out.mat <- ABC_out$param
par.vec.length <- nrow(ABC_out$param)

```

<!--DON'T INCLUDE-->

```{r EASYRUN, eval=FALSE, include=FALSE}
#########################################################
#########################################################
#########################################################
## FUNCTION MODEL.OUTPUT.TO.PLOT.SIM
## Calculates mean and CI of each estimated parameter & CFR/IFR
## Uses correlated.param.SIM
## Reads in Beta(t), Alpha(t), Kappa(t), Delta(t) from file
iter <- 10
time.steps <- 400
vars.to.plot <- vars.plus.R
traj.0 <- model.output.to.plot.SIM(ABC.out.mat=ABC.out.mat, par.vec.length=par.vec.length, iter=iter, time.steps=time.steps, vars.to.plot = vars.to.plot)

## FUNCTION PLOT.ALL.VARIABLES
time.steps.4.plot = 274 #160 
data.in <- latest_data
vars.to.plot <- vars.plus.R

plot.all.variables <- 
plot.model.data.all(traj.CI = traj.0, data.in = data.in, init.date.data = "2020-03-01", date.offset.4plot = 15, time.steps.4plot=time.steps.4.plot, 
                    vars.to.plot=vars.plus.R)
plot.all.variables
```

<!--DON'T INCLUDE-->

```{r EASYRUN_CONTINUED, eval=FALSE, include=FALSE}
date.in <- c("2020-04-01", "2020-05-01", "2020-05-15", "2020-06-01", "2020-06-15", "2020-07-01","2020-07-15", "2020-08-01","2020-08-15",  "2020-09-01", "2020-09-15", "2020-10-01","2020-10-15")
CFR.IFR.plots.out <- CFR.IFR.plots(traj.CI=traj.0, date.in=date.in, y.max.CFR=.1, y.max.IFR = .02)
CFR.plot <- CFR.IFR.plots.out[[1]]
IFR.plot <- CFR.IFR.plots.out[[2]]
tables.out <- summary.table.param.CFR.IFR(traj.CI=traj.0, ABC_out=ABC_out, date.in=date.in, use.mean.select = 1, round.by.in = 4)
table.epi <- tables.out[[1]]
table.epi
tables.out[[2]]

plot.all.variables
CFR.plot+IFR.plot

Fig3.plots <- plot.param.t(ABC_out = ABC_out)
Fig3.plots[[3]]

```


<!--Simulate model-->
<!--Get compartment variables over time with CI-->
<!--Get CFR/IFR-->

```{r include=FALSE}
###################################################################################################
## GET MODEL OUTPUT: traj.0

ABC.out.mat <- ABC_out$param
par.vec.length <- nrow(ABC_out$param)
iter <- 10
time.steps <- 400
vars.to.plot <- vars.plus.R

## FUNCTION MODEL.OUTPUT.TO.PLOT.SIM
## Calculates mean and CI of each estimated parameter & CFR/IFR
## Uses correlated.param.SIM
## Reads in Beta, Alpha, Kappa, Delta from file
traj.0 <- model.output.to.plot.SIM(ABC.out.mat=ABC.out.mat, par.vec.length=par.vec.length, iter=iter, time.steps=time.steps, vars.to.plot = vars.to.plot)

```

# Epidemic model

## Tables: Parameter estimates {.tabset}

```{r include=FALSE}
###################################################################################################
## GET MODEL OUTPUT: summary

tables_code <- path(code.paper.dir, "tables_code_FULL.R")
source(tables_code)

date.in <- c("2020-04-01", "2020-04-10", "2020-04-20",  "2020-05-01", "2020-05-15", "2020-06-01", "2020-06-15", "2020-07-01","2020-07-15", "2020-08-01","2020-08-15",  "2020-09-01", "2020-09-15", "2020-10-01","2020-10-15")

tables.out <- summary.table.param.CFR.IFR(traj.CI=traj.0, ABC_out=ABC_out, date.in=date.in, use.mean.select = 1, round.by.in=4)

```

### $R0, r(t), \mu(t)
```{r}
formattable(tables.out[[1]])
write.csv(tables.out[[1]], file = path(output.dir, "R.r.mu_table.csv"))
```

### $\alpha(t)$, $\kappa(t)$, $\delta(t)$ **

```{r}
formattable(tables.out[[2]])
write.csv(tables.out[[2]], file = path(output.dir, "AKD_t_table.csv"))
```

### CFR and IFR

```{r}
formattable(tables.out[[3]])
write.csv(tables.out[[3]], file = path(output.dir, "CFR_IFR_table.csv"))
```

## Figure: Model fits

Summarizes the epidemic model fit with COVID-19 data for LAC from March 1 through `Sys.Date()` for all disease states across multiple views: New cases, representing new daily incidence; the current number in a compartment at a specific date, relevant for understanding current prevalence rates and comparing with healthcare capacity limitations; and cumulative counts until a specific date. Observed data for available compartments with cases attributable to nursing home residents removed, are plotted as black dots. The figure demonstrates that good model fits are achieved in all compartments across time.

* **New = new daily incidence**
* **Current = current census in compartment** 
* **Cumulative = running total over time**
* Black dots depict COVID-19 data, with counts from outbreaks in nursing homes removed
* The dashed line represents healthcare resource capacity limits

```{r include=FALSE}

###################################################################################################
## Plot all variables faceted

time.steps.4.plot = 274 #160 
data.in <- latest_data
vars.to.plot <- vars.plus.R

plot.all.variables <- 
plot.model.data.all(traj.CI = traj.0, data.in = data.in, init.date.data = "2020-03-01", date.offset.4plot = 15, time.steps.4plot=time.steps.4.plot, 
                    vars.to.plot=vars.plus.R)

pdf(file = path(output.dir, "plot.all.variables.pdf"), width=10, height =10)
plot.all.variables
dev.off()
```

```{r}
plot.all.variables
```


## Figures: Time-Varying Parameters {.tabset}

```{r include=FALSE}

plot_code <- path(code.paper.dir, "plot_R_r_akd_FULL.R")
source(plot_code)
Fig3.plots <- plot.param.t(ABC_out = ABC_out)

pdf(file = path(output.dir, "plot_R_t.pdf"), width=10, height =10)
Fig3.plots[[1]]
dev.off()

pdf(file = path(output.dir, "plot_r_t.pdf"), width=10, height =10)
Fig3.plots[[2]]
dev.off()

pdf(file = path(output.dir, "plot_AKD_t.pdf"), width=10, height =10)
Fig3.plots[[3]]
dev.off()

```

### **Reproductive Number R(t)**

```{r}
Fig3.plots[[1]]
```

### **Fraction of Observed Infections r(t)**

```{r}
Fig3.plots[[2]]
```

### **$\alpha(t)$, $\kappa(t)$, $\delta(t)$**

```{r}
Fig3.plots[[3]]
```

### **Population-Average CFR and IFR**

```{r include=FALSE}

CFR_plot_code <- path(code.paper.dir, "plot_CFR_IFR_FULL.R")
source(CFR_plot_code)

date.in <- c("2020-04-01", "2020-04-10", "2020-04-20",  "2020-05-01", "2020-05-15", "2020-06-01", "2020-06-15", "2020-07-01","2020-07-15", "2020-08-01","2020-08-15",  "2020-09-01", "2020-09-15", "2020-10-01","2020-10-15")
#date.in<-c("2020-04-20","2020-07-20")
CFR.IFR.plots.out <- CFR.IFR.plots(traj.CI=traj.0, date.in=date.in, y.max.CFR = .05, y.max.IFR = .01)

pdf(file = path(output.dir, "CFR_IFR_plot.pdf"), width=10, height =10)
CFR.IFR.plots.out[[1]] + CFR.IFR.plots.out[[2]]
dev.off()
```

```{r}
CFR.IFR.plots.out[[1]] + CFR.IFR.plots.out[[2]]
```


# Risk model



