---
title: "Social Distancing Scenarios"
editor_options: 
  chunk_output_type: console
---

``` {r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.width = 10,
  fig.height = 8,
  echo=FALSE,
  warning=FALSE,
  cache=FALSE,
  message=FALSE)
```

```{r scenarios-evaluated, include=FALSE}

# R0_redux_est <- round(ABC.par.stats$`Frac R0 Mar11`[1] , 2)
# R0_est <- round(ABC.par.stats$R0[1] , 2)
# R0_redux_scenarios <- round(seq(R0_redux_est*100, 100, length.out=7),1)
# incr_current_scenarios <- 100*(R0_redux_scenarios - 100*R0_redux_est) / (100*R0_redux_est)
# R0_eff_scenarios <- round((R0_redux_scenarios/100)*R0_est,2)
# scenario_idx <- seq(1:length(R0_redux_scenarios))-1
# scenarios_table <- cbind(scenario_idx, R0_redux_scenarios, incr_current_scenarios, R0_eff_scenarios)
# colnames(scenarios_table) <- c("Scenario", "% of orig. R0", "% increase from current", "Effective R0")

R0_redux_increase_current <- 2.2

#R0_redux_est <- round(ABC.par.stats$`Frac R0 Mar11`[1] , 3) * R0_redux_increase_current
R0_redux_est <- round(ABC.par.stats$`Frac R0 Mar11`[1] , 3)
R0_est <- round(ABC.par.stats$R0[1] , 3)
#R0_redux_scenarios <- round(seq(R0_redux_est, 1, length.out=7),3)
R0_redux_scenarios <- round(seq(R0_redux_est, 1, length.out=7),3)
incr_current_scenarios <- round((R0_redux_scenarios - (R0_redux_est*2.8)) / (R0_redux_est*3) , 3)
R0_eff_scenarios <- round((R0_redux_scenarios)*R0_est,2)
scenario_idx <- seq(1:length(R0_redux_scenarios))-1
scenarios_table <- as.data.frame(cbind(scenario_idx, R0_redux_scenarios, incr_current_scenarios, R0_eff_scenarios))
colnames(scenarios_table) <- c("Scenario", "Percent orig. R0", "Percent increase from current R0", "Effective R0")

```

### Scenarios evaluated

Here we evaluate the impact of `r length(R0_redux_scenarios)` scenarios, each corresponding to a different contact rate. These scenarios can be understood in terms of:

- **Effective $R0$**: The effective R0 this % decrease corresponds to
- **% of original $R0$**: Percent of the original (pre-social-distancing) $R0$ the effective $R0$ this scenario represents
- **% Increase from current**: Percent increase from current (as of `r Sys.Date()`) level of social distancing / contact rate

```{r, echo=FALSE}

# kable(scenarios_table) %>%
#   kable_styling(bootstrap_options = "striped", full_width = F)

formattable(scenarios_table,
            align=rep("c",NCOL(scenarios_table)),
            list(`Percent orig. R0` = percent,
                 `Percent increase from current R0` = percent))

  
```

```{r scenarios-calculations, include=FALSE}

R0_redux_eval = R0_redux_scenarios

scenario = 2
intervention_date = Sys.Date()
ABC.out.mat <- ABC.out.mat.yesR #!!!
# number.pars.to.use = 400
# iter = 30

number.pars.to.use = 100
iter = 10

time.steps=600

sd.redux = R0_redux_eval[1]
traj.2.May1.0 <- model.output.to.plot.SIM(ABC.out.mat, par.vec.length=number.pars.to.use, iter=iter, time.steps=time.steps, vars.to.plot = vars.plus.R, 
                                       init.date.data="2020-03-01", all=TRUE, scenario.selection = scenario,intervention_date=intervention_date,sd.redux=sd.redux)

sd.redux = R0_redux_eval[2]
traj.2.May1.1 <- model.output.to.plot.SIM(ABC.out.mat, par.vec.length=number.pars.to.use, iter=iter, time.steps=time.steps, vars.to.plot = vars.plus.R, 
                                       init.date.data="2020-03-01", all=TRUE, scenario.selection = scenario,intervention_date=intervention_date,sd.redux=sd.redux)

sd.redux = R0_redux_eval[3]
traj.2.May1.2 <- model.output.to.plot.SIM(ABC.out.mat, par.vec.length=number.pars.to.use, iter=iter, time.steps=time.steps, vars.to.plot = vars.plus.R, 
                                       init.date.data="2020-03-01", all=TRUE, scenario.selection = scenario,intervention_date=intervention_date,sd.redux=sd.redux)

sd.redux = R0_redux_eval[4]
traj.2.May1.3 <- model.output.to.plot.SIM(ABC.out.mat, par.vec.length=number.pars.to.use, iter=iter, time.steps=time.steps, vars.to.plot = vars.plus.R, 
                                       init.date.data="2020-03-01", all=TRUE, scenario.selection = scenario,intervention_date=intervention_date,sd.redux=sd.redux)

sd.redux = R0_redux_eval[5]
traj.2.May1.4 <- model.output.to.plot.SIM(ABC.out.mat, par.vec.length=number.pars.to.use, iter=iter, time.steps=time.steps, vars.to.plot = vars.plus.R, 
                                       init.date.data="2020-03-01", all=TRUE, scenario.selection = scenario,intervention_date=intervention_date,sd.redux=sd.redux)

sd.redux = R0_redux_eval[6]
traj.2.May1.5 <- model.output.to.plot.SIM(ABC.out.mat, par.vec.length=number.pars.to.use, iter=iter, time.steps=time.steps, vars.to.plot = vars.plus.R, 
                                       init.date.data="2020-03-01", all=TRUE, scenario.selection = scenario,intervention_date=intervention_date,sd.redux=sd.redux)

sd.redux = R0_redux_eval[7]
traj.2.May1.6 <- model.output.to.plot.SIM(ABC.out.mat, par.vec.length=number.pars.to.use, iter=iter, time.steps=time.steps, vars.to.plot = vars.plus.R, 
                                       init.date.data="2020-03-01", all=TRUE, scenario.selection = scenario,intervention_date=intervention_date,sd.redux=sd.redux)

ymax.nice <- function(traj, var.to.plot, time.steps.4plot){
  median.of.var <- traj %>% filter(state.name==var.to.plot) %>% filter(date < as.Date("2020-03-01")+time.steps.4plot) %>% select(up_95)
  max.median <- max(median.of.var)
  
  roundUpNice <- function(x, nice=c(1,2,4,5,6,8,10)) {
    if(length(x) != 1) stop("'x' must be of length 1")
    10^floor(log10(x)) * nice[[which(x <= 10^floor(log10(x)) * nice)[[1]]]]
  }
  
  ymax.nice.4plot <- roundUpNice(max.median)
  return(ymax.nice.4plot)
}

ymax.nice.Htot <- ymax.nice(traj.2.May1.6, var.to.plot = "Htot",time.steps.4plot=time.steps.4plot)  
ymax.nice.Q <- ymax.nice(traj.2.May1.6, var.to.plot = "Q",time.steps.4plot=time.steps.4plot)  
ymax.nice.V <- ymax.nice(traj.2.May1.6, var.to.plot = "V",time.steps.4plot=time.steps.4plot)  
ymax.nice.D <- ymax.nice(traj.2.May1.6, var.to.plot = "D",time.steps.4plot=time.steps.4plot)  
ymax.nice.I <- ymax.nice(traj.2.May1.6, var.to.plot = "I",time.steps.4plot=time.steps.4plot)  
ymax.nice.Itot <- ymax.nice(traj.2.May1.6, var.to.plot = "Itot",time.steps.4plot=time.steps.4plot)  


### PLOT OBJECTS

##########################
## Htot

scenario=2
intervention_date = Sys.Date()
use.title=TRUE
plot.capacity=TRUE
time.steps.4plot = 400
var.to.plot="Htot"
ymax=ymax.nice.Htot

scenario.no = 0
sd.redux = R0_redux_eval[1]
traj.CI=traj.2.May1.0
p.H.2.May1.0 <- plot.model.single(traj.CI=traj.CI, data.in=data.in.tmp, init.date.data="2020-03-01", date.offset.4plot=15, 
                                   time.steps.4plot=time.steps.4plot, ymax=ymax, plot.capacity=plot.capacity, var.to.plot=var.to.plot,use.title=use.title,
                                   scenario=scenario, intervention_date=intervention_date, sd.redux=sd.redux, scenario.no = scenario.no)

scenario.no = 1
sd.redux = R0_redux_eval[2]
traj.CI=traj.2.May1.1
p.H.2.May1.1 <- plot.model.single(traj.CI=traj.CI, data.in=data.in.tmp, init.date.data="2020-03-01", date.offset.4plot=15, 
                                   time.steps.4plot=time.steps.4plot, ymax=ymax, plot.capacity=plot.capacity, var.to.plot=var.to.plot,use.title=use.title,
                                   scenario=scenario, intervention_date=intervention_date, sd.redux=sd.redux, scenario.no = scenario.no)
scenario.no = 2
sd.redux = R0_redux_eval[3]
traj.CI=traj.2.May1.2
p.H.2.May1.2 <- plot.model.single(traj.CI=traj.CI, data.in=data.in.tmp, init.date.data="2020-03-01", date.offset.4plot=15, 
                                   time.steps.4plot=time.steps.4plot, ymax=ymax, plot.capacity=plot.capacity, var.to.plot=var.to.plot,use.title=use.title,
                                   scenario=scenario, intervention_date=intervention_date, sd.redux=sd.redux, scenario.no = scenario.no)
scenario.no = 3
sd.redux = R0_redux_eval[4]
traj.CI=traj.2.May1.3
p.H.2.May1.3 <- plot.model.single(traj.CI=traj.CI, data.in=data.in.tmp, init.date.data="2020-03-01", date.offset.4plot=15, 
                                   time.steps.4plot=time.steps.4plot, ymax=ymax, plot.capacity=plot.capacity, var.to.plot=var.to.plot,use.title=use.title,
                                   scenario=scenario, intervention_date=intervention_date, sd.redux=sd.redux, scenario.no = scenario.no)

scenario.no = 4
sd.redux = R0_redux_eval[5]
traj.CI=traj.2.May1.4
p.H.2.May1.4 <- plot.model.single(traj.CI=traj.CI, data.in=data.in.tmp, init.date.data="2020-03-01", date.offset.4plot=15, 
                                   time.steps.4plot=time.steps.4plot, ymax=ymax, plot.capacity=plot.capacity, var.to.plot=var.to.plot,use.title=use.title,
                                   scenario=scenario, intervention_date=intervention_date, sd.redux=sd.redux, scenario.no = scenario.no)
scenario.no = 5
sd.redux = R0_redux_eval[6]
traj.CI=traj.2.May1.5
p.H.2.May1.5 <- plot.model.single(traj.CI=traj.CI, data.in=data.in.tmp, init.date.data="2020-03-01", date.offset.4plot=15, 
                                   time.steps.4plot=time.steps.4plot, ymax=ymax, plot.capacity=plot.capacity, var.to.plot=var.to.plot,use.title=use.title,
                                   scenario=scenario, intervention_date=intervention_date, sd.redux=sd.redux, scenario.no = scenario.no)

scenario.no = 6
sd.redux = R0_redux_eval[7]
traj.CI=traj.2.May1.6
p.H.2.May1.6 <- plot.model.single(traj.CI=traj.CI, data.in=data.in.tmp, init.date.data="2020-03-01", date.offset.4plot=15, 
                                   time.steps.4plot=time.steps.4plot, ymax=ymax, plot.capacity=plot.capacity, var.to.plot=var.to.plot,use.title=use.title,
                                   scenario=scenario, intervention_date=intervention_date, sd.redux=sd.redux, scenario.no = scenario.no)


##########################
## Q


plot.capacity=TRUE
time.steps.4plot = 500
var.to.plot="Q"
ymax=ymax.nice.Q

scenario.no = 0
sd.redux = R0_redux_eval[1]
traj.CI=traj.2.May1.0
p.Q.2.May1.0 <- plot.model.single(traj.CI=traj.CI, data.in=data.in.tmp, init.date.data="2020-03-01", date.offset.4plot=15, 
                                   time.steps.4plot=time.steps.4plot, ymax=ymax, plot.capacity=plot.capacity, var.to.plot=var.to.plot,use.title=use.title,
                                   scenario=scenario, intervention_date=intervention_date, sd.redux=sd.redux, scenario.no = scenario.no)

scenario.no = 1
sd.redux = R0_redux_eval[2]
traj.CI=traj.2.May1.1
p.Q.2.May1.1 <- plot.model.single(traj.CI=traj.CI, data.in=data.in.tmp, init.date.data="2020-03-01", date.offset.4plot=15, 
                                   time.steps.4plot=time.steps.4plot, ymax=ymax, plot.capacity=plot.capacity, var.to.plot=var.to.plot,use.title=use.title,
                                   scenario=scenario, intervention_date=intervention_date, sd.redux=sd.redux, scenario.no = scenario.no)
scenario.no = 2
sd.redux = R0_redux_eval[3]
traj.CI=traj.2.May1.2
p.Q.2.May1.2 <- plot.model.single(traj.CI=traj.CI, data.in=data.in.tmp, init.date.data="2020-03-01", date.offset.4plot=15, 
                                   time.steps.4plot=time.steps.4plot, ymax=ymax, plot.capacity=plot.capacity, var.to.plot=var.to.plot,use.title=use.title,
                                   scenario=scenario, intervention_date=intervention_date, sd.redux=sd.redux, scenario.no = scenario.no)
scenario.no = 3
sd.redux = R0_redux_eval[4]
traj.CI=traj.2.May1.3
p.Q.2.May1.3 <- plot.model.single(traj.CI=traj.CI, data.in=data.in.tmp, init.date.data="2020-03-01", date.offset.4plot=15, 
                                   time.steps.4plot=time.steps.4plot, ymax=ymax, plot.capacity=plot.capacity, var.to.plot=var.to.plot,use.title=use.title,
                                   scenario=scenario, intervention_date=intervention_date, sd.redux=sd.redux, scenario.no = scenario.no)

scenario.no = 4
sd.redux = R0_redux_eval[5]
traj.CI=traj.2.May1.4
p.Q.2.May1.4 <- plot.model.single(traj.CI=traj.CI, data.in=data.in.tmp, init.date.data="2020-03-01", date.offset.4plot=15, 
                                   time.steps.4plot=time.steps.4plot, ymax=ymax, plot.capacity=plot.capacity, var.to.plot=var.to.plot,use.title=use.title,
                                   scenario=scenario, intervention_date=intervention_date, sd.redux=sd.redux, scenario.no = scenario.no)
scenario.no = 5
sd.redux = R0_redux_eval[6]
traj.CI=traj.2.May1.5
p.Q.2.May1.5 <- plot.model.single(traj.CI=traj.CI, data.in=data.in.tmp, init.date.data="2020-03-01", date.offset.4plot=15, 
                                   time.steps.4plot=time.steps.4plot, ymax=ymax, plot.capacity=plot.capacity, var.to.plot=var.to.plot,use.title=use.title,
                                   scenario=scenario, intervention_date=intervention_date, sd.redux=sd.redux, scenario.no = scenario.no)

scenario.no = 6
sd.redux = R0_redux_eval[7]
traj.CI=traj.2.May1.6
p.Q.2.May1.6 <- plot.model.single(traj.CI=traj.CI, data.in=data.in.tmp, init.date.data="2020-03-01", date.offset.4plot=15, 
                                   time.steps.4plot=time.steps.4plot, ymax=ymax, plot.capacity=plot.capacity, var.to.plot=var.to.plot,use.title=use.title,
                                   scenario=scenario, intervention_date=intervention_date, sd.redux=sd.redux, scenario.no = scenario.no)



##########################
## V

plot.capacity=TRUE
time.steps.4plot = 500
var.to.plot="V"
ymax=ymax.nice.V

scenario.no = 0
sd.redux = R0_redux_eval[1]
traj.CI=traj.2.May1.0
p.V.2.May1.0 <- plot.model.single(traj.CI=traj.CI, data.in=data.in.tmp, init.date.data="2020-03-01", date.offset.4plot=15, 
                                   time.steps.4plot=time.steps.4plot, ymax=ymax, plot.capacity=plot.capacity, var.to.plot=var.to.plot,use.title=use.title,
                                   scenario=scenario, intervention_date=intervention_date, sd.redux=sd.redux, scenario.no = scenario.no)

scenario.no = 1
sd.redux = R0_redux_eval[2]
traj.CI=traj.2.May1.1
p.V.2.May1.1 <- plot.model.single(traj.CI=traj.CI, data.in=data.in.tmp, init.date.data="2020-03-01", date.offset.4plot=15, 
                                   time.steps.4plot=time.steps.4plot, ymax=ymax, plot.capacity=plot.capacity, var.to.plot=var.to.plot,use.title=use.title,
                                   scenario=scenario, intervention_date=intervention_date, sd.redux=sd.redux, scenario.no = scenario.no)
scenario.no = 2
sd.redux = R0_redux_eval[3]
traj.CI=traj.2.May1.2
p.V.2.May1.2 <- plot.model.single(traj.CI=traj.CI, data.in=data.in.tmp, init.date.data="2020-03-01", date.offset.4plot=15, 
                                   time.steps.4plot=time.steps.4plot, ymax=ymax, plot.capacity=plot.capacity, var.to.plot=var.to.plot,use.title=use.title,
                                   scenario=scenario, intervention_date=intervention_date, sd.redux=sd.redux, scenario.no = scenario.no)
scenario.no = 3
sd.redux = R0_redux_eval[4]
traj.CI=traj.2.May1.3
p.V.2.May1.3 <- plot.model.single(traj.CI=traj.CI, data.in=data.in.tmp, init.date.data="2020-03-01", date.offset.4plot=15, 
                                   time.steps.4plot=time.steps.4plot, ymax=ymax, plot.capacity=plot.capacity, var.to.plot=var.to.plot,use.title=use.title,
                                   scenario=scenario, intervention_date=intervention_date, sd.redux=sd.redux, scenario.no = scenario.no)

scenario.no = 4
sd.redux = R0_redux_eval[5]
traj.CI=traj.2.May1.4
p.V.2.May1.4 <- plot.model.single(traj.CI=traj.CI, data.in=data.in.tmp, init.date.data="2020-03-01", date.offset.4plot=15, 
                                   time.steps.4plot=time.steps.4plot, ymax=ymax, plot.capacity=plot.capacity, var.to.plot=var.to.plot,use.title=use.title,
                                   scenario=scenario, intervention_date=intervention_date, sd.redux=sd.redux, scenario.no = scenario.no)
scenario.no = 5
sd.redux = R0_redux_eval[6]
traj.CI=traj.2.May1.5
p.V.2.May1.5 <- plot.model.single(traj.CI=traj.CI, data.in=data.in.tmp, init.date.data="2020-03-01", date.offset.4plot=15, 
                                   time.steps.4plot=time.steps.4plot, ymax=ymax, plot.capacity=plot.capacity, var.to.plot=var.to.plot,use.title=use.title,
                                   scenario=scenario, intervention_date=intervention_date, sd.redux=sd.redux, scenario.no = scenario.no)

scenario.no = 6
sd.redux = R0_redux_eval[7]
traj.CI=traj.2.May1.6
p.V.2.May1.6 <- plot.model.single(traj.CI=traj.CI, data.in=data.in.tmp, init.date.data="2020-03-01", date.offset.4plot=15, 
                                   time.steps.4plot=time.steps.4plot, ymax=ymax, plot.capacity=plot.capacity, var.to.plot=var.to.plot,use.title=use.title,
                                   scenario=scenario, intervention_date=intervention_date, sd.redux=sd.redux, scenario.no = scenario.no)



##########################
## D

plot.capacity=NULL
var.to.plot="D"
ymax=ymax.nice.D

scenario.no = 0
sd.redux = R0_redux_eval[1]
traj.CI=traj.2.May1.0
p.D.2.May1.0 <- plot.model.single(traj.CI=traj.CI, data.in=data.in.tmp, init.date.data="2020-03-01", date.offset.4plot=15, 
                                   time.steps.4plot=time.steps.4plot, ymax=ymax, plot.capacity=plot.capacity, var.to.plot=var.to.plot,use.title=use.title,
                                   scenario=scenario, intervention_date=intervention_date, sd.redux=sd.redux, scenario.no = scenario.no)

scenario.no = 1
sd.redux = R0_redux_eval[2]
traj.CI=traj.2.May1.1
p.D.2.May1.1 <- plot.model.single(traj.CI=traj.CI, data.in=data.in.tmp, init.date.data="2020-03-01", date.offset.4plot=15, 
                                   time.steps.4plot=time.steps.4plot, ymax=ymax, plot.capacity=plot.capacity, var.to.plot=var.to.plot,use.title=use.title,
                                   scenario=scenario, intervention_date=intervention_date, sd.redux=sd.redux, scenario.no = scenario.no)
scenario.no = 2
sd.redux = R0_redux_eval[3]
traj.CI=traj.2.May1.2
p.D.2.May1.2 <- plot.model.single(traj.CI=traj.CI, data.in=data.in.tmp, init.date.data="2020-03-01", date.offset.4plot=15, 
                                   time.steps.4plot=time.steps.4plot, ymax=ymax, plot.capacity=plot.capacity, var.to.plot=var.to.plot,use.title=use.title,
                                   scenario=scenario, intervention_date=intervention_date, sd.redux=sd.redux, scenario.no = scenario.no)
scenario.no = 3
sd.redux = R0_redux_eval[4]
traj.CI=traj.2.May1.3
p.D.2.May1.3 <- plot.model.single(traj.CI=traj.CI, data.in=data.in.tmp, init.date.data="2020-03-01", date.offset.4plot=15, 
                                   time.steps.4plot=time.steps.4plot, ymax=ymax, plot.capacity=plot.capacity, var.to.plot=var.to.plot,use.title=use.title,
                                   scenario=scenario, intervention_date=intervention_date, sd.redux=sd.redux, scenario.no = scenario.no)

scenario.no = 4
sd.redux = R0_redux_eval[5]
traj.CI=traj.2.May1.4
p.D.2.May1.4 <- plot.model.single(traj.CI=traj.CI, data.in=data.in.tmp, init.date.data="2020-03-01", date.offset.4plot=15, 
                                   time.steps.4plot=time.steps.4plot, ymax=ymax, plot.capacity=plot.capacity, var.to.plot=var.to.plot,use.title=use.title,
                                   scenario=scenario, intervention_date=intervention_date, sd.redux=sd.redux, scenario.no = scenario.no)
scenario.no = 5
sd.redux = R0_redux_eval[6]
traj.CI=traj.2.May1.5
p.D.2.May1.5 <- plot.model.single(traj.CI=traj.CI, data.in=data.in.tmp, init.date.data="2020-03-01", date.offset.4plot=15, 
                                   time.steps.4plot=time.steps.4plot, ymax=ymax, plot.capacity=plot.capacity, var.to.plot=var.to.plot,use.title=use.title,
                                   scenario=scenario, intervention_date=intervention_date, sd.redux=sd.redux, scenario.no = scenario.no)

scenario.no = 6
sd.redux = R0_redux_eval[7]
traj.CI=traj.2.May1.6
p.D.2.May1.6 <- plot.model.single(traj.CI=traj.CI, data.in=data.in.tmp, init.date.data="2020-03-01", date.offset.4plot=15, 
                                   time.steps.4plot=time.steps.4plot, ymax=ymax, plot.capacity=plot.capacity, var.to.plot=var.to.plot,use.title=use.title,
                                   scenario=scenario, intervention_date=intervention_date, sd.redux=sd.redux, scenario.no = scenario.no)



##########################
## I


plot.capacity=NULL
time.steps.4plot = 500
var.to.plot="I"
ymax=ymax.nice.I

scenario.no = 0
sd.redux = R0_redux_eval[1]
traj.CI=traj.2.May1.0
p.I.2.May1.0 <- plot.model.single(traj.CI=traj.CI, data.in=data.in.tmp, init.date.data="2020-03-01", date.offset.4plot=15, 
                                   time.steps.4plot=time.steps.4plot, ymax=ymax, plot.capacity=plot.capacity, var.to.plot=var.to.plot,use.title=use.title,
                                   scenario=scenario, intervention_date=intervention_date, sd.redux=sd.redux, scenario.no = scenario.no)

scenario.no = 1
sd.redux = R0_redux_eval[2]
traj.CI=traj.2.May1.1
p.I.2.May1.1 <- plot.model.single(traj.CI=traj.CI, data.in=data.in.tmp, init.date.data="2020-03-01", date.offset.4plot=15, 
                                   time.steps.4plot=time.steps.4plot, ymax=ymax, plot.capacity=plot.capacity, var.to.plot=var.to.plot,use.title=use.title,
                                   scenario=scenario, intervention_date=intervention_date, sd.redux=sd.redux, scenario.no = scenario.no)
scenario.no = 2
sd.redux = R0_redux_eval[3]
traj.CI=traj.2.May1.2
p.I.2.May1.2 <- plot.model.single(traj.CI=traj.CI, data.in=data.in.tmp, init.date.data="2020-03-01", date.offset.4plot=15, 
                                   time.steps.4plot=time.steps.4plot, ymax=ymax, plot.capacity=plot.capacity, var.to.plot=var.to.plot,use.title=use.title,
                                   scenario=scenario, intervention_date=intervention_date, sd.redux=sd.redux, scenario.no = scenario.no)
scenario.no = 3
sd.redux = R0_redux_eval[4]
traj.CI=traj.2.May1.3
p.I.2.May1.3 <- plot.model.single(traj.CI=traj.CI, data.in=data.in.tmp, init.date.data="2020-03-01", date.offset.4plot=15, 
                                   time.steps.4plot=time.steps.4plot, ymax=ymax, plot.capacity=plot.capacity, var.to.plot=var.to.plot,use.title=use.title,
                                   scenario=scenario, intervention_date=intervention_date, sd.redux=sd.redux, scenario.no = scenario.no)

scenario.no = 4
sd.redux = R0_redux_eval[5]
traj.CI=traj.2.May1.4
p.I.2.May1.4 <- plot.model.single(traj.CI=traj.CI, data.in=data.in.tmp, init.date.data="2020-03-01", date.offset.4plot=15, 
                                   time.steps.4plot=time.steps.4plot, ymax=ymax, plot.capacity=plot.capacity, var.to.plot=var.to.plot,use.title=use.title,
                                   scenario=scenario, intervention_date=intervention_date, sd.redux=sd.redux, scenario.no = scenario.no)
scenario.no = 5
sd.redux = R0_redux_eval[6]
traj.CI=traj.2.May1.5
p.I.2.May1.5 <- plot.model.single(traj.CI=traj.CI, data.in=data.in.tmp, init.date.data="2020-03-01", date.offset.4plot=15, 
                                   time.steps.4plot=time.steps.4plot, ymax=ymax, plot.capacity=plot.capacity, var.to.plot=var.to.plot,use.title=use.title,
                                   scenario=scenario, intervention_date=intervention_date, sd.redux=sd.redux, scenario.no = scenario.no)

scenario.no = 6
sd.redux = R0_redux_eval[7]
traj.CI=traj.2.May1.6
p.I.2.May1.6 <- plot.model.single(traj.CI=traj.CI, data.in=data.in.tmp, init.date.data="2020-03-01", date.offset.4plot=15, 
                                   time.steps.4plot=time.steps.4plot, ymax=ymax, plot.capacity=plot.capacity, var.to.plot=var.to.plot,use.title=use.title,
                                   scenario=scenario, intervention_date=intervention_date, sd.redux=sd.redux, scenario.no = scenario.no)




##########################
## Itot


plot.capacity=NULL
time.steps.4plot = 500
var.to.plot="Itot"
ymax=ymax.nice.Itot

scenario.no = 0
sd.redux = R0_redux_eval[1]
traj.CI=traj.2.May1.0
p.Itot.2.May1.0 <- plot.model.single(traj.CI=traj.CI, data.in=data.in.tmp, init.date.data="2020-03-01", date.offset.4plot=15, 
                                   time.steps.4plot=time.steps.4plot, ymax=ymax, plot.capacity=plot.capacity, var.to.plot=var.to.plot,use.title=use.title,
                                   scenario=scenario, intervention_date=intervention_date, sd.redux=sd.redux, scenario.no = scenario.no)

scenario.no = 1
sd.redux = R0_redux_eval[2]
traj.CI=traj.2.May1.1
p.Itot.2.May1.1 <- plot.model.single(traj.CI=traj.CI, data.in=data.in.tmp, init.date.data="2020-03-01", date.offset.4plot=15, 
                                   time.steps.4plot=time.steps.4plot, ymax=ymax, plot.capacity=plot.capacity, var.to.plot=var.to.plot,use.title=use.title,
                                   scenario=scenario, intervention_date=intervention_date, sd.redux=sd.redux, scenario.no = scenario.no)
scenario.no = 2
sd.redux = R0_redux_eval[3]
traj.CI=traj.2.May1.2
p.Itot.2.May1.2 <- plot.model.single(traj.CI=traj.CI, data.in=data.in.tmp, init.date.data="2020-03-01", date.offset.4plot=15, 
                                   time.steps.4plot=time.steps.4plot, ymax=ymax, plot.capacity=plot.capacity, var.to.plot=var.to.plot,use.title=use.title,
                                   scenario=scenario, intervention_date=intervention_date, sd.redux=sd.redux, scenario.no = scenario.no)
scenario.no = 3
sd.redux = R0_redux_eval[4]
traj.CI=traj.2.May1.3
p.Itot.2.May1.3 <- plot.model.single(traj.CI=traj.CI, data.in=data.in.tmp, init.date.data="2020-03-01", date.offset.4plot=15, 
                                   time.steps.4plot=time.steps.4plot, ymax=ymax, plot.capacity=plot.capacity, var.to.plot=var.to.plot,use.title=use.title,
                                   scenario=scenario, intervention_date=intervention_date, sd.redux=sd.redux, scenario.no = scenario.no)

scenario.no = 4
sd.redux = R0_redux_eval[5]
traj.CI=traj.2.May1.4
p.Itot.2.May1.4 <- plot.model.single(traj.CI=traj.CI, data.in=data.in.tmp, init.date.data="2020-03-01", date.offset.4plot=15, 
                                   time.steps.4plot=time.steps.4plot, ymax=ymax, plot.capacity=plot.capacity, var.to.plot=var.to.plot,use.title=use.title,
                                   scenario=scenario, intervention_date=intervention_date, sd.redux=sd.redux, scenario.no = scenario.no)
scenario.no = 5
sd.redux = R0_redux_eval[6]
traj.CI=traj.2.May1.5
p.Itot.2.May1.5 <- plot.model.single(traj.CI=traj.CI, data.in=data.in.tmp, init.date.data="2020-03-01", date.offset.4plot=15, 
                                   time.steps.4plot=time.steps.4plot, ymax=ymax, plot.capacity=plot.capacity, var.to.plot=var.to.plot,use.title=use.title,
                                   scenario=scenario, intervention_date=intervention_date, sd.redux=sd.redux, scenario.no = scenario.no)

scenario.no = 6
sd.redux = R0_redux_eval[7]
traj.CI=traj.2.May1.6
p.Itot.2.May1.6 <- plot.model.single(traj.CI=traj.CI, data.in=data.in.tmp, init.date.data="2020-03-01", date.offset.4plot=15, 
                                   time.steps.4plot=time.steps.4plot, ymax=ymax, plot.capacity=plot.capacity, var.to.plot=var.to.plot,use.title=use.title,
                                   scenario=scenario, intervention_date=intervention_date, sd.redux=sd.redux, scenario.no = scenario.no)


```


## Increase contact rate on `r intervention_date` by variable amounts {.tabset}

<br>

In the figures below:

**A dashed line represents healthcare resource capacity limits.**

**Black dots depict COVID-19 data, with counts from outbreaks in nursing homes removed** (for more details see [Data](https://uscbiostats.github.io/COVID19/method.html#data)).

### Scenario 0

Equal to:

- **Effective $R0$**: `r as.numeric(scenarios_table[1,4])`
- **% of original R0**: `r as.numeric(scenarios_table[1,2])*100`
- **% Increase from current**: `r as.numeric(scenarios_table[1,3])*100`

```{r scenario0, echo=FALSE}

ggplotly(p.H.2.May1.0)
ggplotly(p.D.2.May1.0)
ggplotly(p.Q.2.May1.0)
ggplotly(p.V.2.May1.0)
ggplotly(p.I.2.May1.0)
ggplotly(p.Itot.2.May1.0)

```

### Scenario 1

Equal to:

- **Effective $R0$**: `r as.numeric(scenarios_table[2,4])`
- **% of original R0**: `r as.numeric(scenarios_table[2,2])*100`
- **% Increase from current**: `r as.numeric(scenarios_table[2,3])*100`

```{r scenario1, echo=FALSE}

ggplotly(p.H.2.May1.1)
ggplotly(p.D.2.May1.1)
ggplotly(p.Q.2.May1.1)
ggplotly(p.V.2.May1.1)
ggplotly(p.I.2.May1.1)
ggplotly(p.Itot.2.May1.1)

```

### Scenario 2

Equal to:

- **Effective $R0$**: `r as.numeric(scenarios_table[3,4])`
- **% of original R0**: `r as.numeric(scenarios_table[3,2])*100`
- **% Increase from current**: `r as.numeric(scenarios_table[3,3])*100`

```{r scenario2, echo=FALSE}

ggplotly(p.H.2.May1.2)
ggplotly(p.D.2.May1.2)
ggplotly(p.Q.2.May1.2)
ggplotly(p.V.2.May1.2)
ggplotly(p.I.2.May1.2)
ggplotly(p.Itot.2.May1.2)

```

### Scenario 3

Equal to:

- **Effective $R0$**: `r as.numeric(scenarios_table[4,4])`
- **% of original R0**: `r as.numeric(scenarios_table[4,2])*100`
- **% Increase from current**: `r as.numeric(scenarios_table[4,3])*100`

```{r scenario3, echo=FALSE}

ggplotly(p.H.2.May1.3)
ggplotly(p.D.2.May1.3)
ggplotly(p.Q.2.May1.3)
ggplotly(p.V.2.May1.3)
ggplotly(p.I.2.May1.3)
ggplotly(p.Itot.2.May1.3)

```

### Scenario 4

Equal to:

- **Effective $R0$**: `r as.numeric(scenarios_table[5,4])`
- **% of original R0**: `r as.numeric(scenarios_table[5,2])*100`
- **% Increase from current**: `r as.numeric(scenarios_table[5,3])*100`

```{r scenario4, echo=FALSE}

ggplotly(p.H.2.May1.4)
ggplotly(p.D.2.May1.4)
ggplotly(p.Q.2.May1.4)
ggplotly(p.V.2.May1.4)
ggplotly(p.I.2.May1.4)
ggplotly(p.Itot.2.May1.4)

```

### Scenario 5

Equal to:

- **Effective $R0$**: `r as.numeric(scenarios_table[6,4])`
- **% of original R0**: `r as.numeric(scenarios_table[6,2])*100`
- **% Increase from current**: `r as.numeric(scenarios_table[6,3])*100`

```{r scenario5, echo=FALSE}

ggplotly(p.H.2.May1.5)
ggplotly(p.D.2.May1.5)
ggplotly(p.Q.2.May1.5)
ggplotly(p.V.2.May1.5)
ggplotly(p.I.2.May1.5)
ggplotly(p.Itot.2.May1.5)

```

### Scenario 6

Equal to:

- **Effective $R0$**: `r as.numeric(scenarios_table[7,4])`
- **% of original R0**: `r as.numeric(scenarios_table[7,2])*100`
- **% Increase from current**: `r as.numeric(scenarios_table[7,3])*100`

```{r scenario6, echo=FALSE}
ggplotly(p.H.2.May1.6)
ggplotly(p.D.2.May1.6)
ggplotly(p.Q.2.May1.6)
ggplotly(p.V.2.May1.6)
ggplotly(p.I.2.May1.6)
ggplotly(p.Itot.2.May1.6)
```
